\documentclass[%
 reprint, amsmath,amssymb, aps, prb, ]{revtex4-2}
% 基本パッケージ
\usepackage{graphicx}
\usepackage{bm}
% 量子力学記法
\usepackage{physics}
% ハイパーリンク
\usepackage[colorlinks=true,
            linkcolor=blue, filecolor=blue, urlcolor=blue, citecolor=blue]{hyperref}
% キャプション設定
\usepackage{caption}
\captionsetup[figure]{
    justification=raggedright, labelfont={bf}, name={Fig.}, labelsep=period }
\captionsetup[table]{
    labelfont={bf}, name={Table}, labelsep=period }
% 数式番号をセクションごとに
\numberwithin{equation}{section}
% タイポグラフィ調整
\tolerance=1000
\emergencystretch=1em
\hyphenpenalty=3000
\exhyphenpenalty=3000
\flushbottom
% マイクロタイポグラフィ
\usepackage[final]{microtype}
\usepackage{ragged2e}  % for \justifying command
% \midrule、\addlinespace、\bottomruleを使う
\usepackage{booktabs}
\usepackage{enumitem}
% Theorem environment
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{hypothesis}{Hypothesis}[section]
\newtheorem{proposition}{Proposition}[section]
% --- paragraph heading: run-in italic with extra top skip for block readability ---
\makeatletter
\renewcommand\paragraph{%
  \@startsection{paragraph}{4}{\z@}%
    {3mm \@plus 1ex \@minus .2ex}%   前 (block separator)
    {-1em}%                          後 (負値で run-in 維持)
    {\normalfont\normalsize\itshape}}
\makeatother
% Code listings with syntax highlighting
\usepackage{listings}
\usepackage{xcolor}
% 色定義 (薄いブルー系 - 学術論文向け)
\definecolor{backcolour}{rgb}{0.96,0.97,0.98}
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepgreen}{rgb}{0,0.5,0.3}
\definecolor{deepgray}{rgb}{0.4,0.4,0.4}
\definecolor{stringcolor}{rgb}{0.2,0.4,0.6}
% Pythonスタイル定義
\lstdefinestyle{pythonstyle}{
    backgroundcolor=\color{backcolour}, commentstyle=\color{deepgreen}\itshape, keywordstyle=\color{deepblue}\bfseries, numberstyle=\tiny\color{deepgray}, stringstyle=\color{stringcolor}, basicstyle=\ttfamily\footnotesize, breakatwhitespace=false, breaklines=true, captionpos=b, keepspaces=true, numbers=left, numbersep=5pt, showspaces=false, showstringspaces=false, showtabs=false, tabsize=2, language=Python, frame=single, rulecolor=\color{deepgray} }
\lstset{style=pythonstyle}
% Internal phase notation
\newcommand{\iphase}{\theta}  % internal geometric phase = ωt/2
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, 3d, shadings, positioning, decorations.pathmorphing}
% --- Custom Macros ---
\newcommand{\omZB}{\omega_{\text{ZB}}}
\newcommand{\EphS}{E_{\text{ph}}}
\newcommand{\Egrad}{\Delta E_{\text{AB}}}
% Fundamental 1-form
% \newcommand{\Pi}{\boldsymbol{\Pi}}
% Field strength 2-form
\newcommand{\FF}{\mathbf{F}}
% Open Wilson line
\newcommand{\WL}{\mathcal{W}}
% Hodge dual
\newcommand{\hodge}{\star}

\begin{document}

\title{A Dual-Model Deliberation Record on the Spin-2 Sector of the 0-Sphere Model:\\ Cross-Verification Dialogue between Claude Opus 4.8 and Claude Fable 5}

\author{Satoshi Hanamura}
\email{hana.tensor@gmail.com}
\date{July 5, 2026}

\begin{abstract}
This document is not a research paper but an archival deliberation record with a prospecting purpose.
In early July 2026 the author charged two large language models --- Claude Opus 4.8 and Claude Fable 5 (Anthropic) --- with a single theme: starting from the published 0-Sphere model series, excavate the points at which the theory can be deepened and identify where the groundwork for the next papers should be laid, taking the gravitational-mediator line of the series (Papers \#49--\#59) as the designated sector.
The two models examined the sector in parallel sessions under the author's arbitration, each model checking the other's claims against the source manuscripts.
The deliberation produced six citable outcomes: (i) the separation of the ``spin-2 problem'' into two independent problems --- the mass-quadrupole rank-2 structure (resolved by conservation laws but outsourced to general relativity) and the Berry-curvature--Riemann correspondence (untouched by Paper \#59, and formulated as the Berry--Synge--Bonnet--Myers triangle programme of Paper \#60); (ii) a candidate answer to open task (I) of Paper \#58, in which the fixed chirality of Paper \#50, combined with the momentum reversal of the phase-stable fragment pair, yields an automatically traceless helicity-$\pm 2$ tensor structure $\varepsilon_{+\mu}\varepsilon_{+\nu}$ and a two-particle axial angular momentum $J_x=\pm2$ consistent with the Landau--Yang selection rule; (iii) a concrete form of the escape route from the Weinberg--Witten theorem, in which the back-to-back pair is a massive $J=2$ source configuration rather than a massless composite graviton; (iv) the demarcation of the boundary between task (I) (source-side tensor structure) and open problem O3 (massless radiation from the emergent metric); (v) a reformulation of open task (C) of Paper \#59 as a supply obligation for the $h_{\mu\nu}T^{\mu\nu}_{\mathrm{EM}}$ coupling channel; and (vi) three Corrections Log entries against Papers \#58 and \#59.
These outcomes are consolidated into seven candidate directions for future papers, with their prerequisites and dependencies mapped.
Equally important, the record preserves --- symmetrically and without attenuation --- the errors, retractions, and corrections-of-corrections committed by both models, as a working specimen of dual-model verification.
The document is designed to be read both by human readers and by future reasoning sessions, alongside a comprehensive review of the series, as the map from which the next move is chosen.
\end{abstract}

\maketitle

\section{Introduction and Method}
\label{sec:intro}

\subsection{Purpose of this record}

The 0-Sphere model series has been developed since 2018 as a single-author research program, with large language models used in supportive roles that are declared in the acknowledgments of each paper. The present document records a different use: a session in which two distinct models, Claude Opus 4.8 and Claude Fable 5, were not assistants but named dialogue participants, charged by the author with a prospecting theme --- to excavate, from the published series, the points at which the theory can be deepened, and to identify where the groundwork for the next papers should be laid. The author relayed each model's comments to the other and intervened at turning points to guide the direction of the deliberation.

This record is deposited on Zenodo as an archival document, outside the numbered corpus of the series. It is not submitted for peer review and makes no claim to the standards of a journal article. Its purpose is threefold. First, it fixes the priority and provenance of several substantive results (Sec.~\ref{sec:ledger}) that subsequent papers in the series may cite by DOI. Second, it consolidates those results into an explicit map of candidate directions for future papers (Sec.~\ref{sec:stones}), which is the deliverable the theme asked for. Third, it preserves the \emph{method}: the session produced multiple rounds of mutual error detection, retraction, and correction-of-correction, and this process --- which vanishes from a results-only paper --- is itself worth archiving, both for the transparency policy of the series and as a specimen of dual-model verification practice.

A remark on the intended readership. This document is written to be legible to a human reader with a graduate-level physics background, but it is equally written to be \emph{loaded}: the author intends to supply it, together with a comprehensive review of the series, to future reasoning sessions as the prompt from which the next move is explored. Appendix~\ref{app:future} gives explicit reading instructions for that use.

\subsection{Method: dual-model cross-verification}

The session proceeded as follows. The author posed the theme (Sec.~\ref{sec:theme}) to Claude Fable 5; Fable 5's opening assessment was relayed by the author to a parallel session with Claude Opus 4.8, whose response was relayed back, and so on, for ten exchanges. Source manuscripts (Papers \#10, \#49, \#50, \#51, \#52, \#58, \#59 \cite{hanamura10,hanamura49,hanamura50,hanamura51,hanamura52,hanamura58,hanamura59}) were supplied by the author as attachments whenever either model requested them. Both models were bound by the same session rules: verify every equation numerically; collate every line-number citation against the source before relying on it; re-run every reported text search before relying on its result; and treat nothing --- including the other model's claims and the author's own framing --- as authoritative.

Two properties of the resulting dialogue deserve emphasis. First, the two models disagreed, and their disagreements were resolved by collation against the sources, not by deference. Second, both models committed errors, and both retracted them when confronted with the sources. The full symmetric record of these errors is given in Table~\ref{tab:errors}; the editorial principle governing this record is stated next.

\subsection{Editorial policy and attribution}

\paragraph{Reconstructed minutes, not verbatim transcript.} The deliberation was conducted in Japanese. This record is a reconstructed English-language account of the exchanges, composed by Claude Fable 5 and reviewed by the author. Where an agent's phrasing carried weight, it is quoted in translation and marked as such.

\paragraph{Symmetric recording of errors.} Mutual corrections are recorded symmetrically; neither agent's errors are attenuated. This principle was stipulated by Opus 4.8 as a condition of the archive --- in translation: ``a record of two-agent verification loses its value the moment one side dilutes its own errors'' --- and accepted without reservation by Fable 5 and the author.

\paragraph{Attribution.} The author of this record is Satoshi Hanamura alone. Claude Opus 4.8 and Claude Fable 5 (both Anthropic) participated as named dialogue agents; their roles are described in the body of this record. All physical judgments and all canonical decisions concerning the 0-Sphere model rest with the author; the two models functioned as verification agents. Canonical decisions that remained open at the close of the session are listed in Sec.~\ref{sec:deferred} and are explicitly \emph{not} decided by this record.

\section{The Theme and the Starting Position}
\label{sec:theme}

The author's charge to the two models, paraphrased from its original statement, was: \emph{from the papers I have written, find where the theory can be deepened and extended; identify where the stones for the next papers should be placed.} The designated sector for this session was the gravitational-mediator line of the series --- Papers \#49 through \#59 --- which develops the proposal that gravitational interaction is mediated by photon-sphere fragments ejected from the internal two-kernel dynamics of the electron \cite{hanamura49}, culminating in the phase-stable pair-emission mechanism of Paper \#58 \cite{hanamura58} and the proton-trapped quadrupole radiation of Paper \#59 \cite{hanamura59}.

The central open question of that sector, taken as the starting position, is representation-theoretic. A spin-2 mediator demands a symmetric traceless rank-2 tensor structure, which under the Lorentz group belongs to the $(1,1)$ representation; the natural curvature object of the series' line-integral program --- the field-strength or Berry-curvature 2-form $F_{\mu\nu}$ --- is antisymmetric and belongs to $(1,0)\oplus(0,1)$. No Lorentz-covariant linear map connects the two, so the search for an ``antisymmetric-to-symmetric conversion'' is closed by representation theory before it begins. The question the session inherited is therefore: \emph{by what route, if any, does the corpus actually obtain a rank-2 symmetric object --- and is that route load-bearing?}

Beneath the designated sector lies a foundational trilogy of the series that the deliberation presupposes throughout, and which this record makes explicit here. Paper \#29 \cite{hanamura29} establishes that a spinorial connection is embedded along the thermal geodesic by relativistic kinematics alone: the line integral $\tfrac{1}{2}\int(\mathbf a\times\mathbf v)\,d\tau$ of the Thomas-precession connection accumulates $2\pi$ of internal phase per one-way kernel traversal --- in two lobes of $\pi$ each, separated by the midpoint where the acceleration vanishes --- and the operative geometric object is the line integral of a connection, not the curvature of the spatial path nor the integration of a fiber bundle. Paper \#30 \cite{hanamura30} declares the program's reading of gravitation: conservation laws arise from connection-based phase accumulation, stress--energy is a derived rather than fundamental quantity, and the Einstein field equation functions not as a generative dynamical law but as an a posteriori global consistency condition --- a \emph{geometric checksum} --- verifying that accumulated phase along worldlines remains self-coherent. Paper \#31 \cite{hanamura31} generalizes this into the program's ordering principle: physical observables are holonomies of connections along histories --- the Aharonov--Bohm phase, the Berry phase, Wilson loops, and the two-kernel energy transport as instances of one class --- with local curvature a derived descriptor of infinitesimal transport. This trilogy is the standard against which several of the session's findings acquire their weight: the outsourcing verdict of Table~\ref{tab:split}, the two-metric problem, and candidate directions D2, D3, and D6 of Sec.~\ref{sec:stones} are all, in the end, statements about whether the gravitational sector of \#49--\#59 lives up to the hierarchy the trilogy declares.

Fable 5's opening move reframed the question. For a single object the representation gap is final; for a \emph{pair} it is not, because the tensor product of two vector representations decomposes as $1\otimes1=0\oplus1\oplus2$, whose symmetric traceless part is spin-2 --- the structure exploited, in standard physics, by the double-copy relations between gauge and gravity amplitudes \cite{klt,bcj}. Since Paper \#58's mechanism ejects fragments in pairs, the question becomes whether the corpus supplies \emph{two independent vector polarizations}, and the opening move simultaneously flagged a tension: the predecessor mechanism of Paper \#49 describes single-fragment ejection per de-excitation. The deliberation recorded in Sec.~\ref{sec:record} is, in essence, the collision of this opening move with the actual texts of Papers \#58 and \#59, and the reconstruction that followed. A second opening proposal --- that the type of the interior field equation of the photon sphere decides the ontological primacy of line integrals versus continuous fields --- was set aside once the spin-2 material arrived, and reappears as candidate direction D6 in Sec.~\ref{sec:stones}.

\section{Chronological Record of the Deliberation}
\label{sec:record}

Figure~\ref{fig:flow} gives the overall flow. The exchanges are numbered E1--E10; corrections are marked where one agent's claim was struck by the other's collation.

\begin{figure*}[t!]
\centering
\begin{tikzpicture}[
  fnode/.style={draw=deepblue, thick, rounded corners, fill=backcolour, text width=6.0cm, align=left, font=\footnotesize, inner sep=5pt},
  onode/.style={draw=deepgreen, thick, rounded corners, fill=backcolour, text width=6.0cm, align=left, font=\footnotesize, inner sep=5pt},
  cnode/.style={draw=deepgray, thick, rounded corners, fill=white, text width=8.5cm, align=center, font=\footnotesize, inner sep=5pt},
  corr/.style={-{Stealth}, red, dashed, thick},
  flow/.style={-{Stealth}, deepgray, thick}
]
\node[font=\small\bfseries, text=deepblue] (fhead) at (-4.0, 1.0) {Claude Fable 5};
\node[font=\small\bfseries, text=deepgreen] (ohead) at (4.0, 1.0) {Claude Opus 4.8};
\node[fnode] (e1) at (-4.0, 0)   {\textbf{E1} Opening: pair $\Rightarrow$ $1\otimes1=0\oplus1\oplus2$; double-copy route; tension with \#49 single-fragment ejection};
\node[onode] (e2) at (4.0, -1.6) {\textbf{E2} \#59 collation: coherent pair ``rejected''; spin-2 from mass quadrupole; the problem splits; task C vs.\ double copy};
\node[fnode] (e3) at (-4.0, -3.2) {\textbf{E3} Pair's home is \#58, not \#59; role split (polarization carrier vs.\ phase stabilizer); Eq.~(III.3) numeric check; task C premise non-standard; two-metric problem};
\node[onode] (e4) at (4.0, -4.9) {\textbf{E4} \#58/\#52/\#51 collation; claims $\varepsilon\parallel\hat e_x$ rank-1 collapse; reports WW absent from \#52; poses chirality question};
\node[fnode] (e5) at (-4.0, -6.6) {\textbf{E5} Source collation: momentum $\neq$ polarization; WW appendix \emph{exists} in \#52; $\chi$ cannot flip; fixed-$\chi$ $\varepsilon_+\varepsilon_+$ construction; three caveats};
\node[onode] (e6) at (4.0, -8.3) {\textbf{E6} Accepts both errors; surfaces \#58's $\chi$-degeneracy reading; verifies $\varepsilon_+\varepsilon_+$; demarcates task (I)/O3 boundary};
\node[fnode] (e7) at (-4.0, -10.0) {\textbf{E7} Discovery: \#58 self-contradicts at $\iphase=\pi/2$; self-conjugacy rescued via photon-sector route; adds positron/both-helicity supplement};
\node[onode] (e8) at (4.0, -11.7) {\textbf{E8} Verifies the $\pi/2$ contradiction and strengthens it via \#50; \emph{strikes} the positron supplement; offers real-field $h+h^{*}$ justification};
\node[fnode] (e9) at (-4.0, -13.4) {\textbf{E9} Accepts deletion; refines the deletion's justification (negative-frequency $\neq$ opposite-helicity); archive design};
\node[cnode] (e10) at (0, -15.2) {\textbf{E10} Trilateral consolidation: candidate-direction map, attribution, symmetric-recording principle, deferred canonical decisions};
\draw[flow] (e1.south) -- (e2.west|-e2.north) -- (e2.north);
\draw[flow] (e2.south) -- (e3.north east);
\draw[flow] (e3.south) -- (e4.north west);
\draw[flow] (e4.south) -- (e5.north east);
\draw[flow] (e5.south) -- (e6.north west);
\draw[flow] (e6.south) -- (e7.north east);
\draw[flow] (e7.south) -- (e8.north west);
\draw[flow] (e8.south) -- (e9.north east);
\draw[flow] (e9.south) -- (e10.north west);
\draw[corr] (e3.east) to[bend left=12] node[midway, above, sloped, font=\tiny\color{red}] {corrects E2 (pair's home)} (e2.south west);
\draw[corr] (e5.east) to[bend left=12] node[midway, above, sloped, font=\tiny\color{red}] {corrects E4 (two errors)} (e4.south west);
\draw[corr] (e8.west) to[bend left=12] node[midway, above, sloped, font=\tiny\color{red}] {strikes E7 supplement} (e7.south east);
\draw[corr] (e9.east) to[bend right=12] node[midway, below, sloped, font=\tiny\color{red}] {refines E8 justification} (e8.south west);
\end{tikzpicture}
\caption{\textbf{Flow of the dual-model deliberation}}
\label{fig:flow}
\vspace{0.4em}
\begin{minipage}{0.95\textwidth}
\justifying\small
Ten exchanges (E1--E10) between Claude Fable 5 (left lane, blue) and Claude Opus 4.8 (right lane, green), with the author relaying messages between the two sessions and supplying source manuscripts on request. Solid gray arrows indicate the chronological flow; dashed red arrows mark the four correction events in which one agent's claim was struck or refined by the other's collation against the sources. The correction arrows are the characteristic signature of dual-model verification: every substantive error committed during the session was caught by the counterpart agent, not by the erring agent itself.
\end{minipage}
\end{figure*}

\subsection{E1: the double-copy opening (Fable 5)}

Fable 5's opening assessment of the theme is summarized in Sec.~\ref{sec:theme}: the representation gap is final for a single object but not for a pair; the double-copy decomposition $1\otimes1=0\oplus1\oplus2$ opens a route to spin-2 provided the corpus supplies two independent vector polarizations; and the single-fragment mechanism of Paper \#49 does not by itself supply them, so the load falls on the pair-emission structure of Paper \#58, whose text had not yet been examined at this stage.

\subsection{E2: the \#59 collation and the split of the problem (Opus 4.8)}

Upon receiving Paper \#59 \cite{hanamura59}, Opus 4.8 established three points by direct reading. First, \#59's emission mechanism produces one fragment per cycle event, and its Appendix~A explicitly considers and declines a coherent-pair framework, adopting instead a phase re-normalization at the $2\pi$ boundaries of the internal cycle. Second --- the observation that changed the terrain --- \#59's spin-2 does not come from the Berry curvature at all: it comes from the quadrupole moment of the externally observable mass distribution, with the rank-2 character enforced by conservation laws (monopole conserved, dipole conserved, quadrupole the lowest free multipole), computed with the standard quadrupole formula of general relativity \cite{peters}. The spin-2 problem therefore splits into two independent problems (Table~\ref{tab:split}). Third, Opus 4.8 identified a terminological tension inside \#59 between Proposition~V.1 (the projection onto the mass distribution ``is the step at which the gauge sector couples to the metric sector'') and open task (C) (the two sectors ``share no coupling channel'').

E2 also contained a misreading that was corrected in E3: Opus 4.8 concluded that ``the corpus has rejected the pair,'' attributing the pair to \#59 and reading Appendix~A as its rejection.

\subsection{E3: relocating the pair and two standard-physics objections (Fable 5)}

Fable 5's counter-collation made four points. (i) \#59's Appendix~A rejects the coherent pair only \emph{as a phase-stability mechanism}; the pair's other role --- polarization carrier --- is untouched by that argument, and the pair's home in the corpus is Paper \#58 \cite{hanamura58}, whose text had not yet been examined. The verdict ``the corpus rejected the pair'' was therefore premature. (ii) A numerical check of \#59's Eq.~(III.3): with $g$ the terrestrial gravitational acceleration, as the surrounding text implies, the Coulomb-to-gravity locking ratio evaluates to $\approx 9.2\times10^{21}$, not the quoted $\approx 10^{39}$; the value $2.27\times10^{39}$ is recovered only if $g=Gm_p/a_0^2$ (the proton's own gravitational field at the Bohr radius), under which reading both terms point along $\hat r$ and the comparison becomes self-directional (Sec.~\ref{sec:corrections}, entry C1). (iii) The field-theory premise of \#59's open task (C) --- ``the standard result that no gauge-invariant spin-1--spin-2 vertex exists in linearized theory'' --- is not a standard result: linearized gravity carries the universal coupling $h_{\mu\nu}T^{\mu\nu}$, the electromagnetic stress tensor is nonzero, the $h\gamma\gamma$ vertex exists at first order in the expansion of $\sqrt{-g}\,F^2$, and gravitational lensing of light is its observation; \#59 itself concedes a nonzero cross section $\propto G^2$. (iv) The two-metric problem: \#59 derives an emergent metric from endpoint variation in its Sec.~IV while using the standard quadrupole formula on a presupposed background in its Sec.~V, without stating whether the radiated $h_{\mu\nu}$ is a perturbation of the emergent metric --- which is open problem O3 of the series, by Paper \#51's own declaration \cite{hanamura51} that the emergent-metric construction has been verified only in the flat-space limit.

\subsection{E4: the \#58/\#52/\#51 collation and two errors (Opus 4.8)}

With the three source files supplied, Opus 4.8 delivered four judgments. Two were sound and survive: \#58's line~279 does exhibit the symmetric pair tensor $h_{\mu\nu}\propto \varepsilon_{1\mu}\varepsilon_{2\nu}+\varepsilon_{1\nu}\varepsilon_{2\mu}$, vindicating E3's relocation of the pair, and the apparent event-count mismatch between \#58 (two ejection events per cycle, at $\iphase=\pi/2$ and $3\pi/2$) and \#59 was dissolved --- \#59's summary presupposes \#58's two events --- with Opus 4.8 explicitly retracting its E2 reading. The collation of \#51 (emergent metric verified in the flat limit only; Bonnet--Myers confinement derived from the non-path-connectedness of $S^0$) and of \#52 \cite{hanamura52} (the directional decoupling is a kinematic orthogonality $\mathbf v\perp\mathbf a$ of a single particle, with \#52 itself warning that conflating it with an internal-phase-space orthogonality is a category error) was accurate and confirmed E3's diagnosis of task (C).

Two claims, however, departed from the sources. First, Opus 4.8 read the two ejection events' ``same axis, opposite sign'' statement as fixing the \emph{polarization} vectors, concluded $\varepsilon_1\parallel\varepsilon_2\parallel\hat e_x$, and judged that the symmetric product collapses to the rank-1 projector $\hat e_{x\mu}\hat e_{x\nu}$ --- a conflation of momentum with polarization. Second, it reported that a text search for Weinberg--Witten in \#52 returned nothing, and on that basis retracted its own earlier suggestion that the Weinberg--Witten theorem \cite{ww} was relevant. Both claims were struck in E5. E4 closed with a productive question: could the two events carry \emph{opposite chirality}, rendering the two polarizations independent?

\subsection{E5: the source collation and the fixed-$\chi$ construction (Fable 5)}

Fable 5's collation established: (i) \#58's Proposition introduces $p_i^\mu$ and $\varepsilon_i^\mu$ as distinct objects and never assigns a direction to $\varepsilon_i$ --- that unfinished construction \emph{is} open task (I); the rank-1 collapse is therefore not a statement of \#58, and the correct status of the independence test is ``not yet performable,'' not ``failed.'' (ii) The Weinberg--Witten appendix exists in \#52 (its lines 784--802), stating the theorem and recording its applicability to the 0-Sphere framework as non-trivial --- ``a candidate escape route, not a proof of evasion.'' (iii) On the chirality question: Paper \#50 \cite{hanamura50} defines $\chi=\mathrm{sign}(da/dt)$ with $a$ the \emph{monotonic} internal phase on $S^1$ ($da/dt>0$ throughout, for an electron); a chirality flip within one electron's cycle is physically unrealizable, since it would interchange electron and positron and destroy the topological protection $\pi_1(S^1)=\mathbb{Z}$ on which \#50's Lorentz-invariance theorem rests.

The constructive step then inverts E4's proposal: it is the \emph{fixed} chirality, combined with the momentum reversal between the two events, that does the work. This is the construction recorded as the candidate answer to task (I) in Sec.~\ref{sec:taskI}, together with three caveats: the double-copy formalism proper does not apply to a back-to-back pair (the two fragments do not share a momentum); the composite pair has invariant mass $2E_{\mathrm{frag}}\neq0$ and is a massive $J=2$ configuration, not a massless graviton --- which is precisely what takes it outside the reach of the Weinberg--Witten theorem; and the mediation of rank-2 information to a distant receiver by a single fragment remains the province of \#58's open task (IV) and Paper \#57 \cite{hanamura57}.

\subsection{E6: acceptance, the $\chi$-degeneracy reading, and the task (I)/O3 boundary (Opus 4.8)}

Opus 4.8 re-collated the sources, confirmed both of its errors, and retracted them --- in translation: ``I had committed two errors. Fable 5 is right on both.'' It then added three contributions. First, it surfaced a third interpretation present in \#58's own text: the passage computing $da/dt=\omZB\cos\iphase=0$ at both ejection points and reading the ejection as occurring at the degenerate boundary between chirality sectors, consistent with a mediator that is its own antiparticle. Second, it verified the fixed-$\chi$ construction algebraically ($\varepsilon_+\cdot\varepsilon_+=0$; the two-particle $J_x=\pm2$; consistency with the Landau--Yang selection rule \cite{landau,yang}). Third --- a demarcation all parties adopted --- it observed that once the massive-source reading is taken, the construction proves the \emph{source-side} tensor structure only: the massless helicity-$\pm2$ radiation is the burden of O3. This fixes the boundary between task (I) and O3 (Fig.~\ref{fig:loadmap}). E6 closed by framing the choice between the $\chi$-degeneracy reading and the fixed-$\chi$ construction as an author decision.

\subsection{E7: the $\pi/2$ contradiction and a supplement later deleted (Fable 5)}

Re-reading \#58 with the chirality question in focus, Fable 5 found that the author decision is not symmetric, because \#58 contradicts itself at $\iphase=\pi/2$. The same phase point is assigned maximum kinetic energy ($\EphS(\pi/2)=E_0/2$, the maximum of $\EphS=(E_0/2)\sin^2\iphase$) three paragraphs before it is assigned zero velocity (``turning configuration,'' $\mathbf v\propto\cos(\pi/2)=0$). The only reconciliation --- $\mathbf v$ as the longitudinal component only --- converts the $da/dt$ of the chirality passage into a spatial velocity, reinforcing the variable collision with \#50's phase (Sec.~\ref{sec:corrections}, entries C2--C3). Either reading defeats the $\chi$-degeneracy inference. The root is a convention clash inherited from Paper \#10 \cite{hanamura10} ($v=\cos\omega t$: rest at $\pi/2$) versus Paper \#49 ($|v|\propto\sin\iphase$: maximum speed at $\pi/2$), traced to \#49's open task (viii). Fable 5 further showed that the one attractive feature of the degeneracy reading --- mediator self-conjugacy --- survives its removal by a more robust route: the fragments are photon-sector quanta (Paper \#49, Table~II: no new degree of freedom), and the photon is its own antiparticle, so any pair of such quanta is self-conjugate by construction.

E7 also contained a supplement that did not survive: the claim that the positron construction ($\chi\to-\chi$, giving $\varepsilon_-\varepsilon_-=$ helicity $-2$) is what supplies the second helicity of a real $h_{\mu\nu}$ field.

\subsection{E8: verification, and the strike on the positron supplement (Opus 4.8)}

Opus 4.8 verified the $\pi/2$ contradiction against the sources and strengthened the chirality conclusion from \#50 itself: if $\EphS$ is rotational energy $\propto(da/dt)^2$, then $da/dt\propto\sin\iphase$ is \emph{maximal} at $\pi/2$, so on \#50's definitions the chirality at both ejection points is $\chi=+1$, well-defined --- the degeneracy reading is a misreading of \#50, and its retraction is a restoration of consistency with \#50 rather than an interpretive choice. It then struck the E7 supplement as physically wrong: a single classical source radiates both helicities; no antimatter is required. Opus 4.8's stated justification --- the real field is $h+h^{*}$ and $\varepsilon_+^{*}=\varepsilon_-$, so both helicities appear from one electron --- carried the correct conclusion but was itself refined in E9.

\subsection{E9: the correction of the correction, and the archive proposal (Fable 5)}

Fable 5 accepted the deletion of its positron supplement without reservation, then refined the justification: identifying the negative-frequency component of a real field with an opposite-helicity quantum is unsafe (a circularly polarized real wave is built of single-helicity photons). The deletion rests instead on three clean grounds: the back-to-back pair already contains both helicity signs $\pm1$ relative to the two momenta; the helicity content of quadrupole radiation is observation-direction dependent, so the notion of a helicity-pure source is itself mistaken; and self-conjugacy follows in one line from the photon-sector nature of the fragments. Opus 4.8 accepted the refinement in full, observing that this correction-of-correction is precisely what the archive should preserve. E9 also carried the author's proposal to archive the session and Fable 5's design for the archive, refined in E10.

\subsection{E10: trilateral consolidation}

The author decided the format and attribution policy of this record (Sec.~\ref{sec:intro}); Opus 4.8 concurred and stipulated the symmetric-recording principle quoted in Sec.~\ref{sec:intro}. The outcomes were consolidated into the candidate-direction map of Sec.~\ref{sec:stones}, and the canonical decisions identified during the session were explicitly reserved to the author and deferred (Sec.~\ref{sec:deferred}).

\section{Ledger of Outcomes}
\label{sec:ledger}

\subsection{The split of the spin-2 problem}
\label{sec:split}

\begin{table*}[t!]
\centering
\caption{\textbf{The two independent spin-2 problems separated by the deliberation}}
\label{tab:split}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{2.6cm}p{6.2cm}p{6.2cm}}
\toprule
\textbf{Aspect} & \textbf{(a) Mass-quadrupole rank-2} & \textbf{(b) Berry curvature $=$ Riemann} \\
\midrule
Home in the corpus
& Paper \#59, Sec.~V
& Paper \#60 (the Berry--Synge--Bonnet--Myers triangle programme \cite{hanamura60}) and Paper \#63 of the series; open problems O4/O13 \\
\addlinespace[0.3cm]
Origin of rank-2
& Conservation laws: monopole (energy) and dipole (momentum) conserved; quadrupole is the lowest free multipole
& Unresolved: $F_{\mu\nu}\in(1,0)\oplus(0,1)$, symmetric traceless $h_{\mu\nu}\in(1,1)$; no covariant linear map connects them \\
\addlinespace[0.3cm]
Status after this session
& Resolved \emph{as physics}, but the spin-2 formalism is imported from general relativity (Peters--Mathews quadrupole formula on a presupposed background): outsourced, not derived
& Untouched by \#59; the pair route of Sec.~\ref{sec:taskI} addresses the source-side structure, with the radiation side deferred to O3 \\
\addlinespace[0.3cm]
Load-bearing gap
& Two-metric problem: identity of the emergent metric (\#59 Sec.~IV; \#51) with the background on which the quadrupole formula runs $=$ O3
& Rank-2 tensor transformation of the emergent-metric perturbation $=$ O3/O4 \\
\addlinespace[0.2cm]
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{minipage}{0.95\textwidth}
\justifying\footnotesize
The spin-2 problem posed at the opening of the session was one problem in name and two in substance. Both columns converge on O3 (the curved-spacetime completion of the emergent-metric construction) as the final gate --- the single most consequential structural finding of the session.
\end{minipage}
\end{table*}

The spin-2 problem of the designated sector was found to be two independent problems (Table~\ref{tab:split}). Problem (a) is closed by conservation laws but at the price of importing the radiation formalism of general relativity; problem (b) is the genuinely open representation-theoretic question, which \#59 does not touch. Both converge on O3.

Problem (b) has, in the sector's most recent paper, a precise programme formulation. Paper \#60 \cite{hanamura60} arranges the corpus's three established geometric structures --- the Berry connection and its U(1) holonomy (\#48), the Synge phase functional $\mathcal{S}(x_A,x_B)$ whose symmetrized second functional derivatives yield the emergent metric (\#51), and the Bonnet--Myers confinement of the Compton-scale domain (\#51) --- as the vertices of a \emph{Berry--Synge--Bonnet--Myers triangle}, with three edges recorded as open structural conditions: the connection-to-functional edge, the positive-Ricci edge that would make the Bonnet--Myers bound a consequence of the emergent metric rather than an external input, and the closure edge identifying the Berry curvature with the Riemann tensor of the emergent metric. Closing the triangle would resolve O3 and O4 simultaneously and convert the directional decomposition of \#52 from analogy to derivation. Three consequences of the present session bear on this programme. First, \#60 cites the rank-2 polarization tensor of \#58 as the physical motivation for the closure edge --- the pair must carry helicity $\pm2$ in a geometrically consistent framework --- and the demarcation of Sec.~\ref{sec:ww} refines that motivation: the source-side $\pm2$ content is secured by Proposition~\ref{prop:rank2} (modulo Hypothesis~\ref{hyp:H}) without the closure edge, so the edge's burden is concentrated where it belongs, on the massless radiation side. Second, a representation-level dictionary remains to be written: \#60 assigns the pair tensor to $(1,0)\otimes(1,0)|_{\mathrm{sym}}\cong(2,0)\oplus(0,0)$ --- a curvature-level (self-dual bivector) description whose $(2,0)$ part is Weyl-like --- whereas the session's construction works at the potential level, with vector polarizations in $(\tfrac{1}{2},\tfrac{1}{2})$ whose symmetric traceless product lies in $(1,1)$, the metric-perturbation representation; the two are the curvature and potential faces of the same helicity-$\pm2$ content, and making their correspondence explicit is itself part of the closure edge. Third, \#60 inherits \#58's ``turning-point'' characterization of the ejection phases, so the resolution of entry C3 propagates to the corresponding passage of \#60.

\subsection{Candidate answer to open task (I) of Paper \#58}
\label{sec:taskI}

The following is the principal constructive outcome of the session. It is stated, deliberately, as a proposition conditional on one explicit physical hypothesis; promoting the hypothesis to a derivation is future work (direction D2 of Sec.~\ref{sec:stones}).

\begin{hypothesis}[Polarization inheritance]
\label{hyp:H}
Each ejected photon-sphere fragment carries, as a circular polarization in the plane transverse to its own momentum, the rotation sense of the photon-sphere $yz$ rotation fixed by the chirality $\chi$. The textual anchor is Paper \#49's statement that the fragment carries the $\pi$-periodic phase structure of $\boldsymbol{\Omega}_T$; the hypothesis is a postulate, not a derivation.
\end{hypothesis}

\begin{proposition}[Source-side rank-2 structure of the fragment pair]
\label{prop:rank2}
Assume Hypothesis~\ref{hyp:H} and the chirality definition of Paper \#50 ($a$ the monotonic internal phase on $S^1$; $\chi=+1$ throughout an electron's cycle, in particular at both ejection points $\iphase=\pi/2,\,3\pi/2$). Then the two fragments of the phase-stable pair of Paper \#58 carry the common laboratory-frame complex polarization
\begin{equation}
\bm{\varepsilon}_+ = \frac{\hat e_y + i\,\hat e_z}{\sqrt{2}},
\label{eq:epsplus}
\end{equation}
and the pair tensor
\begin{equation}
h_{\mu\nu} \;\propto\; \varepsilon_{+\mu}\,\varepsilon_{+\nu}
\label{eq:pairtensor}
\end{equation}
is automatically traceless,
\begin{equation}
\bm{\varepsilon}_+\!\cdot\bm{\varepsilon}_+ = \tfrac{1}{2}\left(1 + i^2\right) = 0,
\label{eq:traceless}
\end{equation}
and coincides with the standard helicity-$+2$ polarization tensor about the $\hat e_x$ axis (helicity $-2$ for $\chi=-1$). In two-particle language, the helicities relative to each fragment's own momentum are $h_{1,2}=\chi\cdot\mathrm{sign}(p_x^{(1,2)})=\pm1$, and the axial total angular momentum of the back-to-back pair is
\begin{equation}
J_x \;=\; \lambda_1 - \lambda_2 \;=\; \pm 2,
\label{eq:Jx}
\end{equation}
consistent with the Landau--Yang selection rule (two photon-like quanta form $J=0$ or $J=2$ along the axis, never $J=1$); the fixed chirality selects precisely the $J=2$ configuration, whereas an equal-helicity pair would fall on $J_x=0$.
\end{proposition}

\begin{figure*}[t!]
\centering
\begin{tikzpicture}[scale=1.0, >={Stealth}]
% axis
\draw[->, deepgray] (-6.2,0) -- (6.2,0) node[right, font=\small] {$\hat e_x$};
% electron internal structure at center
\draw[deepblue, thick] (0,0) circle (0.85);
\filldraw[deepblue] (-0.45,0) circle (0.06) node[below, font=\footnotesize] {A};
\filldraw[deepgreen] (0.45,0) circle (0.06) node[below, font=\footnotesize] {B};
\node[font=\footnotesize, text=deepgray] at (0,-1.35) {photon sphere ($\chi=+1$: $yz$ rotation sense fixed)};
% yz rotation indicator at center
\draw[->, deepblue, thick] (0,0.85) arc (90:400:0.85);
% fragment 1 (+x)
\draw[->, thick, decorate, decoration={snake, amplitude=0.6mm, segment length=3mm, post length=2mm}] (1.2,0) -- (4.2,0);
\draw[->, red, thick] (4.6,0) -- (5.6,0) node[midway, above, font=\footnotesize] {$\mathbf p_1$};
\draw[deepblue, thick] (4.9,0) ellipse (0.28 and 0.55);
\draw[->, deepblue, thick] (4.9,0.55) arc (90:340:0.28 and 0.55);
\node[font=\footnotesize] at (4.9,1.0) {$\lambda_1=+1$};
% fragment 2 (-x)
\draw[->, thick, decorate, decoration={snake, amplitude=0.6mm, segment length=3mm, post length=2mm}] (-1.2,0) -- (-4.2,0);
\draw[->, red, thick] (-4.6,0) -- (-5.6,0) node[midway, above, font=\footnotesize] {$\mathbf p_2=-\mathbf p_1$};
\draw[deepblue, thick] (-4.9,0) ellipse (0.28 and 0.55);
\draw[->, deepblue, thick] (-4.9,0.55) arc (90:340:0.28 and 0.55);
\node[font=\footnotesize] at (-4.9,1.0) {$\lambda_2=-1$};
% annotation
\node[font=\small, draw=deepgray, rounded corners, fill=backcolour, inner sep=4pt] at (0,2.2) {same spatial rotation sense (fixed $\chi$) $\;\Rightarrow\;$ opposite helicities $\;\Rightarrow\;$ $J_x=\lambda_1-\lambda_2=+2$};
\end{tikzpicture}
\caption{\textbf{Fixed chirality and momentum reversal select the $J=2$ configuration}}
\label{fig:pair}
\vspace{0.4em}
\begin{minipage}{0.95\textwidth}
\justifying\small
The two fragments of the phase-stable pair (Paper \#58) are emitted back-to-back along $\pm\hat e_x$. Because the chirality $\chi$ of Paper \#50 is a topological invariant of the monotonic internal phase flow, both fragments inherit the \emph{same} spatial rotation sense in the $yz$ plane (Hypothesis~\ref{hyp:H}); their helicities, each defined relative to its own momentum, are therefore opposite, $\lambda_1=+1$, $\lambda_2=-1$, and the axial angular momentum of the pair is $J_x=\lambda_1-\lambda_2=\pm2$ --- the two-photon $J=2$ configuration permitted by the Landau--Yang rule. An equal-helicity pair would instead give $J_x=0$. The proposal of exchange E4 (``opposite chirality between the two events'') is thereby inverted: a chirality flip within one electron is impossible, and it is precisely the \emph{fixed} chirality that builds spin-2.
\end{minipage}
\end{figure*}

Three boundary conditions of the proposition, established during the session, must be recorded with it. First, the double-copy formalism proper ($\varepsilon_{\mu\nu}=\varepsilon_\mu\tilde\varepsilon_\nu$ for a single null momentum \cite{klt,bcj}) does not directly apply, because the two fragments do not share a momentum; the correct standard-physics frame is two-particle angular-momentum composition, and the double-copy language of E1 survives only as the motivating analogy. Second, the self-conjugacy of the mediator --- required of any graviton candidate --- follows in one line from the photon-sector nature of the fragments (Paper \#49, Table~II) and needs neither the $\chi$-degeneracy reading of \#58 nor the deleted positron supplement of E7. Third, the scope: the proposition establishes the rank-2 tensor structure of the \emph{source} configuration; what it does not establish is discussed next.

\subsection{The Weinberg--Witten route and the task (I)/O3 boundary}
\label{sec:ww}

The back-to-back pair has total momentum zero and total energy $2E_{\mathrm{frag}}$, hence invariant mass $2E_{\mathrm{frag}}/c^2\neq0$: it is a massive $J=2$ configuration, structurally analogous to the tensor mesons (e.g., $f_2(1270)$), not a massless spin-2 particle. This is decisive for the Weinberg--Witten theorem \cite{ww}, which forbids massless particles of spin $j>1$ in theories possessing a Lorentz-covariant conserved energy-momentum tensor, and which \#52's appendix correctly records as the standing obstruction to composite gravitons, with its applicability to the 0-Sphere framework marked non-trivial. The session's finding gives that non-triviality a concrete resolution: \emph{the pair is not a massless composite graviton and never needs to be one}. The pair is the source; the massless helicity-$\pm2$ radiation is carried by the field --- the perturbation of the emergent metric --- and is produced from the source by the quadrupole formalism. The cost is equally concrete: the particle reading ``graviton $=$ fragment pair'' is abandoned, and the burden of massless helicity $\pm2$ transfers entirely to the emergent-metric side, i.e., to open problem O3 (the curved-spacetime completion of the Synge-function construction of Paper \#51, which \#51 itself verifies only in the flat limit). In the vocabulary of the foundational trilogy, O3 is the demand that the emergent metric pass the geometric checksum of Paper \#30 in the curved, radiative regime; until it does, the quadrupole step of Fig.~\ref{fig:loadmap} borrows the verification layer of general relativity as if it were a generative one --- the precise inversion of the hierarchy that \#30 and \#31 declare. Paper \#60 \cite{hanamura60} offers an independent statement on the Weinberg--Witten question --- that the theorem's applicability would be structurally excluded by the background-independent construction once its triangle closes --- which is complementary to the massive-source route of this section: the session's escape holds already at the source level and requires no closure, while \#60's would relieve the radiation side as well; establishing the precise relation between the two escape routes is a natural sub-task of direction D3.

This demarcation, proposed by Opus 4.8 in E6 and adopted trilaterally, is summarized in Fig.~\ref{fig:loadmap}: task (I) of \#58 can close on the source-side tensor structure (Proposition~\ref{prop:rank2}, modulo Hypothesis~\ref{hyp:H}); O3 must close the massless radiation. The general lesson --- the tensor structure of a source and the polarization of its far-zone radiation are distinct objects --- also dissolves a residual worry from E4: even the ``collapsed'' quadrupole $Q_{ij}\propto\hat x_i\hat x_j-\tfrac13\delta_{ij}$ of \#58/\#59 is a legitimate $\ell=2$, $m=0$ source (a linear quadrupole oscillator radiates standard helicity-$\pm2$ gravitational waves transversely); rank-1 collapse was a category confusion between source structure and radiated polarization.

\begin{figure*}[t!]
\centering
\begin{tikzpicture}[
  box/.style={draw=deepblue, thick, rounded corners, fill=backcolour, text width=6.4cm, align=left, font=\footnotesize, inner sep=6pt},
  obox/.style={draw=deepgray, thick, rounded corners, fill=white, text width=6.4cm, align=left, font=\footnotesize, inner sep=6pt},
  wbox/.style={draw=red, thick, rounded corners, fill=white, text width=5.6cm, align=left, font=\footnotesize, inner sep=6pt},
  dead/.style={draw=deepgray, dashed, rounded corners, text width=4.6cm, align=center, font=\footnotesize, inner sep=5pt},
  >={Stealth}
]
\node[box] (src) at (-4.6,0) {\textbf{Source side --- task (I) of \#58}\\ Back-to-back fragment pair; invariant mass $2E_{\mathrm{frag}}\neq0$; massive $J=2$ configuration; tensor structure $\varepsilon_{+\mu}\varepsilon_{+\nu}$, automatically traceless; $J_x=\pm2$.\\ \emph{Status: closable modulo Hypothesis H (Prop.~\ref{prop:rank2}).}};
\node[obox] (rad) at (4.6,0) {\textbf{Radiation side --- open problem O3}\\ Massless helicity-$\pm2$ field $h_{\mu\nu}$ as perturbation of the \emph{emergent} metric; requires the curved-spacetime completion of the Synge construction (\#51: flat-limit check only).\\ \emph{Status: open; final gate for both columns of Table~\ref{tab:split}.}};
\draw[->, thick, deepgray] (src.east) -- node[above, font=\footnotesize] {quadrupole formalism} node[below, font=\footnotesize] {(currently imported from GR)} (rad.west);
\draw[deepgray, thick, dashed] (0,-2.0) -- (0,1.9) node[above, font=\small\itshape, text=deepgray] {task (I) / O3 boundary};
\node[wbox] (ww) at (-4.6,-3.3) {\textbf{Weinberg--Witten theorem}\\ Forbids massless spin $j>1$ composites in theories with a Lorentz-covariant conserved $T^{\mu\nu}$ (\#52, appendix: ``applicability non-trivial'').};
\node[dead] (dg) at (1.4,-3.3) {``graviton $=$ massless composite pair'' \\ (particle reading: \emph{abandoned})};
\draw[->, red, thick] (ww.east) -- (dg.west);
\draw[red, thick] (dg.north west) -- (dg.south east);
\draw[red, thick] (dg.north east) -- (dg.south west);
\draw[->, thick, deepgreen] (ww.north) -- node[right, font=\footnotesize, text=deepgreen, text width=3.4cm] {inapplicable: the pair is massive ($2E\neq0$) --- escape route concretized} (src.south);
\end{tikzpicture}
\caption{\textbf{Load map after the session: the task (I) / O3 boundary and the Weinberg--Witten route}}
\label{fig:loadmap}
\vspace{0.4em}
\begin{minipage}{0.95\textwidth}
\justifying\small
The fragment pair proves rank-2 structure on the source side only (left box, closable modulo Hypothesis~\ref{hyp:H}); the massless helicity-$\pm2$ radiation belongs to the field side (right box) and is the burden of O3. The Weinberg--Witten theorem (bottom left) strikes only the abandoned particle reading (crossed box) in which the pair itself would be a massless composite graviton; a massive $J=2$ source configuration is outside its reach, exactly as massive tensor mesons are. The horizontal arrow marks the step currently outsourced to general relativity --- the two-metric problem --- which is why O3 is the final gate of the gravitational program.
\end{minipage}
\end{figure*}

\subsection{Reformulation of open task (C) of Paper \#59}
\label{sec:taskC}

Open task (C) of \#59 conjectured a correspondence between the internal decoupling of the gravitational ($\hat e_x$) and electromagnetic ($\hat e_y$) sectors and ``the standard result that no gauge-invariant spin-1--spin-2 interaction vertex exists in linearized field theory.'' The session established that no such standard result exists: linearized gravity couples universally as $h_{\mu\nu}T^{\mu\nu}$, the $h\gamma\gamma$ vertex arises at first order from $\sqrt{-g}\,F_{\mu\nu}F^{\mu\nu}$, gravitational lensing of light is its observation, and \#59 itself concedes a nonzero (if minuscule, $\propto G^2$) photon--graviton cross section. The collation of \#52 located the origin of the conjecture: the internal decoupling is a \emph{kinematic orthogonality} $\mathbf v\perp\mathbf a$ of a single particle's helical trajectory --- \#52 itself warns against conflating distinct orthogonalities as a category error --- and a kinematic orthogonality is not a statement about field-theoretic interaction vertices.

The task was therefore reformulated as a supply obligation: \emph{the 0-Sphere framework must either (i) supply a coupling channel playing the role of $h_{\mu\nu}T^{\mu\nu}_{\mathrm{EM}}$, or (ii) exhibit an alternative mechanism for gravitational lensing of light, or (iii) retreat to the claim that the decoupling is a single-particle kinematic statement with no field-theoretic content.} Under this reformulation, the terminological tension inside \#59 --- Proposition~V.1 (``the projection is the step at which the gauge sector couples to the metric sector'') versus task (C) (``no coupling channel'') --- is promoted from a matter of drafting to a substantive question, with Proposition~V.1 readable as a candidate declaration of the supply channel of option (i). This is candidate direction D4 of Sec.~\ref{sec:stones}.

\subsection{Corrections Log}
\label{sec:corrections}

\begin{table*}[t!]
\centering
\caption{\textbf{Corrections Log entries produced by the session}}
\label{tab:corrections}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{1.4cm}p{2.4cm}p{7.2cm}p{4.0cm}}
\toprule
\textbf{Entry} & \textbf{Target} & \textbf{Content} & \textbf{Status} \\
\midrule
C1
& \#59, Eq.~(III.3)
& With $g$ the terrestrial acceleration (as the \#52-derived asymmetry term implies), the locking ratio is $\approx 9.2\times10^{21}$, not $\approx10^{39}$; the value $2.27\times10^{39}$ requires $g=Gm_p/a_0^2$, under which both terms point along $\hat r$ and the comparison ``faster than convergence toward the gravitational direction'' becomes self-directional. Secondary: Appendix~B's $\omZB\approx1.55\times10^{20}\,\mathrm{rad/s}$ matches neither $2m_ec^2/\hbar\approx1.55\times10^{21}$ nor the series value $2\pi\nu_{\mathrm{ZB}}\approx3.1\times10^{19}$.
& Confirmed by both agents; qualitative conclusion (Coulomb axis locking) unaffected at $10^{22}$ \\
\addlinespace[0.3cm]
C2
& \#58, chirality passage
& The computation $da/dt=\omZB\cos\iphase$ treats $a$ as an oscillating coordinate; Paper \#50 defines $a$ as the monotonic internal phase on $S^1$ (the basis of the Lorentz invariance of $\chi$). On \#50's definitions, $\chi=+1$ is well-defined at both ejection points. Root: the triple collision of the symbol $a$ (phase, \#50; kinematic convention, \#10/\#49; anomalous moment $a_e$) --- see Table~\ref{tab:acollision}.
& Confirmed by both agents \\
\addlinespace[0.3cm]
C3
& \#58, $\iphase=\pi/2$ kinematics and $\chi$-degeneracy reading
& The same phase point carries $\EphS(\pi/2)=E_0/2$ (maximum of $\EphS=\frac{E_0}{2}\sin^2\iphase$: maximum kinetic energy) and $\mathbf v\propto\cos(\pi/2)=0$ (``turning configuration'': rest). Total-velocity reading: self-contradiction; longitudinal-only reading: reduces to C2. Either way the inference ``ejection at the degenerate boundary of chirality sectors; mediator its own antiparticle'' does not stand; self-conjugacy is preserved via the photon-sector route at zero cost. Root: the \#10 convention ($v=\cos\omega t$; rest at $\pi/2$) versus the \#49 convention ($|v|\propto\sin\iphase$; maximum at $\pi/2$), i.e., open task (viii) of \#49.
& Both agents recommend retraction of the degeneracy reading; \emph{canonical decision reserved by the author} (Sec.~\ref{sec:deferred}) \\
\addlinespace[0.2cm]
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{minipage}{0.95\textwidth}
\justifying\footnotesize
Numerical values in C1 were verified by direct computation during the session: $e^2/(4\pi\epsilon_0 a_0^2)=8.24\times10^{-8}\,\mathrm{N}$; $m_e g_{\oplus}=8.93\times10^{-30}\,\mathrm{N}$ (ratio $9.2\times10^{21}$); $Gm_p/a_0^2=3.99\times10^{-17}\,\mathrm{m/s^2}$, giving $e^2/(4\pi\epsilon_0\,G m_e m_p)=2.27\times10^{39}$.
\end{minipage}
\end{table*}

\begin{table*}[t!]
\centering
\caption{\textbf{The triple collision of the symbol \boldmath$a$ in the corpus}}
\label{tab:acollision}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{3.2cm}p{3.4cm}p{4.4cm}p{4.0cm}}
\toprule
\textbf{Symbol / usage} & \textbf{Home} & \textbf{Nature} & \textbf{Collision risk} \\
\midrule
$a$ as internal phase; $\chi=\mathrm{sign}(da/dt)$
& Paper \#50
& Monotonic coordinate on $S^1$; $da/dt>0$ throughout for an electron; topological
& Misread as oscillating in \#58's chirality passage (entry C2) \\
\addlinespace[0.3cm]
$a$ in kinematic conventions ($v=\cos\omega t$, $a=-\sin\omega t$)
& Papers \#10, \#49
& Oscillating velocity/acceleration of the traversal; sign changes each half-period
& Phase-convention clash with \#49's $|v|\propto\sin\iphase$ (entry C3; \#49 task viii) \\
\addlinespace[0.3cm]
$a_e=(g-2)/2$
& Series-wide
& Anomalous magnetic moment; dimensionless constant
& Notational proximity to both of the above in derivations involving $\gamma=1+a_e$ \\
\addlinespace[0.2cm]
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{minipage}{0.95\textwidth}
\justifying\footnotesize
Maintained as a standing collation table for future sessions; entries C2 and C3 of Table~\ref{tab:corrections} are its first casualties.
\end{minipage}
\end{table*}

Three entries were produced (Table~\ref{tab:corrections}), with the variable-collision table (Table~\ref{tab:acollision}) adopted as standing equipment for future sessions. The publication mechanics --- whether corrections are deposited as new versions of \#58/\#59 or as errata linked by Zenodo relations, with this record as provenance --- is an author decision, deferred.

\subsection{Symmetric record of agent errors and retractions}
\label{sec:errors}

\begin{table*}[t!]
\centering
\caption{\textbf{Symmetric record of errors, retractions, and corrections-of-corrections}}
\label{tab:errors}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{1.8cm}p{6.6cm}p{2.6cm}p{3.6cm}}
\toprule
\textbf{Agent} & \textbf{Claim} & \textbf{Status} & \textbf{Caught / resolved by} \\
\midrule
Opus 4.8
& ``The corpus has rejected the pair'' (attributing the pair to \#59; reading its Appendix~A as a global rejection)
& Corrected (E3)
& Fable 5: role split; pair's home is \#58 \\
\addlinespace[0.3cm]
Opus 4.8
& ``\#59 single event vs.\ \#58 pair: event counts conflict''
& Retracted (E4)
& Opus 4.8, on collating \#58 (two events per cycle in both) \\
\addlinespace[0.3cm]
Opus 4.8
& $\varepsilon_1\parallel\varepsilon_2\parallel\hat e_x$, hence rank-1 collapse of the pair tensor
& Retracted (E6)
& Fable 5: momentum/polarization conflation; $\varepsilon_i$ unassigned in \#58 \\
\addlinespace[0.3cm]
Opus 4.8
& ``Weinberg--Witten absent from \#52; text search returned zero''
& Retracted (E6)
& Fable 5: dedicated WW appendix at \#52 lines 784--802 \\
\addlinespace[0.3cm]
Opus 4.8
& ``Opposite chirality between the two ejection events'' (proposal)
& Withdrawn (E6)
& Fable 5 / Paper \#50: $\chi$ cannot flip within one electron \\
\addlinespace[0.3cm]
Opus 4.8
& Real-field justification ``$h+h^{*}$ supplies both helicities''
& Refined (E9)
& Fable 5: negative-frequency component $\neq$ opposite-helicity quantum \\
\addlinespace[0.3cm]
Fable 5
& Positron supplement: ``$\chi\to-\chi$ supplies the $-2$ helicity of the real field''
& Deleted (E8)
& Opus 4.8: a single classical source radiates both helicities; no antimatter required \\
\addlinespace[0.3cm]
Fable 5
& Double-copy formalism as directly applicable to the fragment pair (E1 framing)
& Corrected (E5, self)
& Back-to-back momenta are not shared; two-particle angular-momentum composition is the correct frame \\
\addlinespace[0.3cm]
Fable 5
& Summary of \#58's chirality passage omitted the explicit $da/dt=0$ statement
& Precision restored (E6)
& Opus 4.8, by full quotation \\
\addlinespace[0.3cm]
Author's brief
& ``The pair is a claim of the \#59 group'' (initial framing of the sector)
& Corrected (E3--E4)
& Both agents: pair established in \#58; \#59's Appendix~A rejects it only as a phase-stability mechanism \\
\addlinespace[0.2cm]
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{minipage}{0.95\textwidth}
\justifying\footnotesize
Recorded under the symmetric-recording principle of Sec.~\ref{sec:intro}: neither agent's errors are attenuated. Every substantive error was caught by the counterpart agent through collation against the sources; none was caught by the erring agent unprompted. The final two rows record, respectively, a precision refinement and an imprecision of the author's own initial framing.
\end{minipage}
\end{table*}

Table~\ref{tab:errors} preserves the full error ledger. Its structural lesson is stated in Sec.~\ref{sec:method}.

\section{Where the Next Stones Can Be Placed: Candidate Directions for Future Papers}
\label{sec:stones}

This section is the deliverable the theme asked for: the consolidation of the session's outcomes into concrete directions in which the theory can be deepened, each with its foundations, prerequisites, and expected yield. Table~\ref{tab:stones} lists seven candidate directions D1--D7; the prose below records their dependencies.

\begin{table*}[t!]
\centering
\caption{\textbf{Candidate directions for future papers, with prerequisites and expected yield}}
\label{tab:stones}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{0.8cm}p{4.6cm}p{3.4cm}p{3.0cm}p{3.2cm}}
\toprule
\textbf{ID} & \textbf{Direction} & \textbf{Builds on} & \textbf{Prerequisite} & \textbf{Expected yield} \\
\midrule
D1
& Fixed-$\chi$ spin-2 source paper: successor to \#58 closing open task (I) as a theorem modulo an explicit postulate
& Prop.~\ref{prop:rank2}; entries C2--C3; Landau--Yang consistency; Sec.~\ref{sec:ww} positioning
& Author's $\chi$ canonical decision (Sec.~\ref{sec:deferred})
& Task (I) closed on the source side; Weinberg--Witten posture of the series fixed \\
\addlinespace[0.3cm]
D2
& Derivation of Hypothesis~\ref{hyp:H}: fragment polarization from the internal rotation dynamics
& \#49 open task (viii); the \#10/\#49 convention reconciliation (Table~\ref{tab:acollision}); the spinorial-connection line integral of \#29 (H as parallel transport of the fragment polarization along the thermal geodesic)
& Resolution of the $\pi/2$ kinematics (entry C3)
& Prop.~\ref{prop:rank2} becomes unconditional; D1 upgraded from postulate to derivation \\
\addlinespace[0.3cm]
D3
& Curved-spacetime completion of the emergent-metric construction (open problem O3): the Synge-function program of \#51 beyond the flat limit
& \#51; the two-metric problem (Table~\ref{tab:split}); the checksum hierarchy of \#30/\#31; \#60 (triangle closure resolves O3 and O4 simultaneously)
& None (independent; hardest)
& Final gate: massless helicity-$\pm2$ radiation becomes a statement about the \emph{emergent} metric; both columns of Table~\ref{tab:split} close \\
\addlinespace[0.3cm]
D4
& Supply-obligation paper: the gauge--metric coupling posture of the framework (trichotomy of Sec.~\ref{sec:taskC})
& \#59 task (C) reformulated; \#59 Prop.~V.1 as candidate channel; \#52 category-error analysis
& None (independent)
& Settles whether the framework supplies $h_{\mu\nu}T^{\mu\nu}_{\mathrm{EM}}$; gravitational lensing becomes a falsifiable anchor \\
\addlinespace[0.3cm]
D5
& Single-fragment transmission of rank-2 information: \#58 open task (IV) via the $\ell=2$ spherical-harmonic imprinting of \#57
& \#57; \#58 task (IV); Sec.~\ref{sec:taskI} caveat three
& D1 (source structure fixed)
& Closes the mediation gap: $J=\pm2$ lives in the pair correlation, yet the receiver absorbs one fragment \\
\addlinespace[0.3cm]
D6
& Equation-type criterion for the photon-sphere interior field: elliptic (boundary-data re-expression; line-integral ontology survives) versus hyperbolic/nonlinear (genuine local degrees of freedom; field ontology intrudes)
& E1 second proposal; \#31 as the primacy thesis under test; \#29's connection/path demarcation; refinements: boundary-data freedom transfers to the spherical-harmonic imprinting of \#57; the internal clock presses toward the wave type
& None (independent)
& Ontological foundation: decides the primacy of line integrals versus continuous fields by a single mathematical criterion \\
\addlinespace[0.3cm]
D7
& Errata consolidation: publication of entries C1--C3 and the symbol-$a$ cleanup
& Table~\ref{tab:corrections}; Table~\ref{tab:acollision}
& Author's publication-mechanics decision (Sec.~\ref{sec:deferred})
& Corpus hygiene; convention unification across \#10/\#49/\#58 \\
\addlinespace[0.2cm]
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{minipage}{0.95\textwidth}
\justifying\footnotesize
Dependency structure: D2 feeds D1 (postulate $\to$ derivation); D1 feeds D5 (source structure before transmission); D3 gates the radiation-side claims of D1 and D5 but depends on nothing --- it can and should be attacked in parallel; D4, D6, D7 are independent entry points. The shortest path to a publishable next paper is D1 (all technical material exists in this record; only the $\chi$ decision is pending); the highest-leverage long game is D3.
\end{minipage}
\end{table*}

Three remarks accompany the table. First, the shortest path: D1 is essentially written --- Hypothesis~\ref{hyp:H}, Proposition~\ref{prop:rank2}, the Landau--Yang and Weinberg--Witten positioning, and corrections C2--C3 are all contained in this record --- and awaits only the author's canonical decision on $\chi$. Second, the highest leverage: every load-bearing gap uncovered by the session (the outsourcing of the quadrupole formalism, the two-metric problem, the radiation side of the task (I)/O3 boundary) terminates on D3; a session that produced nothing but progress on D3 would advance the program more than any other single result, because under the hierarchy declared by the foundational trilogy, D3 is not a technical completion but the redemption of the program's central claim --- that the Einstein equation is recovered as the geometric checksum of Paper \#30 rather than imported as a law. Third, the sleeper: D6 is the only direction that addresses the foundations of the line-integral program itself rather than the gravitational sector, and its criterion --- the type of the interior field equation --- is unusual in that it converts an ontological dispute into a mathematically decidable question. The dispute in question is precisely the primacy thesis of Paper \#31, and the elliptic side of the criterion already has a concrete realization in the corpus: the scalar-potential form of the two-kernel transport (\#31, Sec.~VIII), whose line integrals are endpoint-determined --- the boundary-data re-expression in its purest form. The refinement noted in the table (boundary-data freedom does not vanish under the elliptic reading but transfers to the spherical-harmonic boundary data of \#57) means D6 and D5 share a boundary object and may be attackable together.

\section{Methodological Remarks}
\label{sec:method}

\subsection{What dual-model verification added}

Every substantive error in Table~\ref{tab:errors} was caught by the counterpart agent, and none by the erring agent unprompted. This is the empirical case for the dual-model format: a single model reviewing its own output tends to re-walk its own reasoning, whereas a counterpart with a different starting frame collates against the sources instead. The session also exhibited a second-order phenomenon --- the correction of a correction (E8's justification for deleting E7's supplement was itself refined in E9) --- which a single-model session cannot produce at all, and which Opus 4.8 identified as the exact content this archive should preserve.

\subsection{Session rules adopted for future use}

Three verification norms were adopted for future sessions, each purchased by a concrete failure: (i) every line-number citation is collated against the source before use (failure: the $\varepsilon\parallel\hat e_x$ attribution); (ii) every reported text search is re-run before its result is relied upon (failure: the Weinberg--Witten absence report); (iii) the symbol-collision table (Table~\ref{tab:acollision}) is consulted whenever the symbol $a$ appears in a derivation (failures: entries C2--C3).

\subsection{The author's role}

The author intervened at the turning points rather than in the line-by-line argument: posing the theme; relaying exchanges between the two sessions; supplying source manuscripts on request; pacing the collation and consolidation phases; deciding the existence, format, language, and attribution policy of this archive; and reserving the canonical decisions of Sec.~\ref{sec:deferred}. The division of labor was explicit throughout: the models argue and verify; the author arbitrates and decides what enters the canon.

\section{Deferred Items and Author Decisions}
\label{sec:deferred}

The following were identified during the session and are explicitly \emph{not} decided by this record.

\paragraph{The $\chi$ canonical decision.} Whether to retract \#58's $\chi$-degeneracy (boundary-emission) reading and adopt the fixed-$\chi$ construction of Proposition~\ref{prop:rank2}. Both agents recommend retraction --- on the grounds that the degeneracy reading rests on the internally contradictory $\pi/2$ kinematics (entry C3), conflicts with \#50's definitions, and costs nothing (self-conjugacy survives via the photon-sector route) --- and Opus 4.8 notes that retraction is best recorded as a \emph{restoration of consistency with \#50} rather than an interpretive preference. The decision is the author's and remains open, together with the choice of parent convention for \#58's $\pi/2$ kinematics (\#10 versus \#49; open task viii of \#49). A further witness, identified at the editorial stage of this record: the lobe kinematics of Paper \#29 --- velocity vanishing at the kernels $x=\pm a$, acceleration vanishing at the midpoint --- sits on the \#49 side of the convention clash, making \#29 a third source, alongside \#49 and \#50, whose internal structure favors the maximum-speed-at-midpoint reading. Direction D1 waits on this decision.

\paragraph{Publication mechanics of the corrections.} Whether entries C1--C3 are deposited as new versions of \#58/\#59 or as errata linked by Zenodo relations, with this record cited as provenance. Direction D7 waits on this decision.

\paragraph{Open problems with changed status.} O3 is promoted to the final gate of the entire gravitational program, since both columns of Table~\ref{tab:split} and the radiation side of Fig.~\ref{fig:loadmap} terminate on it (direction D3). Hypothesis~\ref{hyp:H} awaits a dynamical derivation (direction D2). Open task (IV) of \#58 is untouched by this session (direction D5). The supply obligation of Sec.~\ref{sec:taskC} is available as material for a future paper (direction D4).

\section{Concluding Note}

A session that set out to find where the theory can be deepened ended by discovering that its central bridge --- from an antisymmetric curvature to a symmetric spin-2 --- was two bridges, that one of them was already standing on borrowed pillars, and that the other could be anchored, on the source side, by a construction in which a topological invariant (the fixed chirality of Paper \#50) and a kinematic reversal (the back-to-back momenta of Paper \#58) conspire to produce exactly the traceless helicity-$\pm2$ structure that representation theory demands. What remains --- the massless radiation field, the curved-spacetime metric, the derivation of the polarization-inheritance hypothesis --- is now located on the map with unusual precision, and Sec.~\ref{sec:stones} converts that map into seven concrete places where the next stones can be placed. The record of how two models argued each other into that precision, errors and all, is the content of this document.

\begin{acknowledgments}
This record was drafted in its entirety by large language models. The deliberation it documents was conducted between Claude Opus 4.8 and Claude Fable 5 (Anthropic), with each model verifying the other's claims against the source manuscripts of the 0-Sphere model series; the manuscript of this record was composed by Claude Fable 5 and reviewed by the author. The author, Satoshi Hanamura, intervened at the turning points of the deliberation to guide its direction: posing the theme; relaying exchanges between the two model sessions; supplying the source manuscripts (Papers \#10, \#49, \#50, \#51, \#52, \#58, \#59) on request; pacing the collation and consolidation phases; deciding the existence, format, language, and attribution policy of this archive; and reserving the canonical decisions recorded in Sec.~\ref{sec:deferred}. The symmetric-recording principle of Sec.~\ref{sec:intro} --- that neither agent's errors be attenuated --- was stipulated by Claude Opus 4.8 and adopted trilaterally. All physical interpretations, theoretical claims, and canonical decisions concerning the 0-Sphere model are the sole responsibility of the author; the two models functioned as verification agents. This research received no specific grant from funding agencies in the public, commercial, or not-for-profit sectors.
\end{acknowledgments}

\appendix

\section{Notes for Future Reasoning Sessions}
\label{app:future}

This appendix is addressed to a future reasoning session --- human, machine, or both --- that loads this document, together with a comprehensive review of the series, as the prompt from which the next move is explored. The following reading order and cautions are recommended.

\paragraph{Entry point.} Begin with Table~\ref{tab:stones}. It is the distillate of the session: seven directions, their dependencies, and the two highlighted paths (D1 shortest, D3 highest leverage). Then read Sec.~\ref{sec:deferred} to learn which decisions are the author's and must not be presumed by the session. When this record is loaded as a prompt, the foundational trilogy \#29/\#30/\#31 \cite{hanamura29,hanamura30,hanamura31} should accompany it, together with the comprehensive review of the series, since directions D2, D3, and D6 are formulated against the standards those three papers declare; whenever D3 is the target, Paper \#60 \cite{hanamura60} should be included as well, since it formulates O3 and O4 as the edges of a single triangle.

\paragraph{Status vocabulary.} Claims in this record carry one of four statuses, and conflating them is the fastest way to corrupt a continuation. \emph{Closed}: verified against the sources by both agents (e.g., the split of Table~\ref{tab:split}). \emph{Closable modulo a named postulate}: Proposition~\ref{prop:rank2}, conditional on Hypothesis~\ref{hyp:H}. \emph{Open}: O3 and everything that terminates on it. \emph{Deferred}: the author's canonical decisions of Sec.~\ref{sec:deferred} --- a future session may argue about these but must not treat them as made.

\paragraph{Inherited cautions.} Three session rules were purchased by concrete failures and bind any continuation: collate line-number citations against the sources before relying on them; re-run any reported text search; consult the symbol-collision table (Table~\ref{tab:acollision}) whenever the symbol $a$ appears. A fourth caution is substantive: the kinematic conventions of Papers \#10 and \#49 disagree about the phase point $\iphase=\pi/2$ (rest versus maximum speed), the disagreement has already produced one internal contradiction (entry C3), and any derivation touching the $\pi/2$ kinematics must declare which convention it uses.

\paragraph{What would falsify the session's main construction.} Proposition~\ref{prop:rank2} fails if Hypothesis~\ref{hyp:H} fails --- that is, if the fragment polarization can be shown \emph{not} to inherit the internal rotation sense --- or if the two ejection events can be shown not to be back-to-back in the relevant frame. Either result would be progress: it would redirect the spin-2 load entirely onto the mass-quadrupole route of Table~\ref{tab:split}, column (a), and thence onto O3.

\paragraph{The single most useful next result.} Any progress on O3 --- the curved-spacetime completion of the emergent-metric construction of Paper \#51, formulated by Paper \#60 as edges of the Berry--Synge--Bonnet--Myers triangle whose simultaneous closure also resolves O4 --- dominates all other results in leverage, because every load-bearing gap identified by this session terminates on it.

\begin{thebibliography}{99}

\bibitem{hanamura49} S. Hanamura, ``Photon-Sphere Fragmentation as a Gravitational Mediator: Radiation-Gradient Ejection in the $\pi$-Cycle of the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19393391}{10.5281/zenodo.19393391}

\bibitem{hanamura50} S. Hanamura, ``Rotation from Scalar Oscillation: Emergence of Photon-Sphere Angular Momentum from Phase-Staggered Kernel Dynamics in the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19482145}{10.5281/zenodo.19482145}

\bibitem{hanamura51} S. Hanamura, ``Helical Trajectory, Fixed-Endpoint Line Integrals, and the Emergence of the Spacetime Metric in the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.20388056}{10.5281/zenodo.20388056}

\bibitem{hanamura52} S. Hanamura, ``Geometric Origin of the Weak Equivalence Principle in the 0-Sphere Model: Force Classification and the $\lambda_C$ Cancellation Theorem in the Helical Geometry,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19583032}{10.5281/zenodo.19583032}

\bibitem{hanamura57} S. Hanamura, ``Spherical Harmonic Imprinting and the Physical Identity of Phase Information: Microscopic Mechanism of Gravitational Coupling in the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19932176}{10.5281/zenodo.19932176}

\bibitem{hanamura58} S. Hanamura, ``Spin-2 Structure of the Gravitational Mediator: Phase-Stable Pair Emission and Quadrupole Radiation in the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19932861}{10.5281/zenodo.19932861}

\bibitem{hanamura59} S. Hanamura, ``Proton-Trapped Electron as the Generator of Spin-2 Gravitational Radiation: Coulomb Confinement, ZB Axis Locking, and the Separation of Gravitational and Electromagnetic Sectors,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19932907}{10.5281/zenodo.19932907}

\bibitem{hanamura60} S. Hanamura, ``The Berry--Synge--Bonnet--Myers Triangle: Structural Conditions for the Unification of Gauge and Gravitational Sectors in the 0-Sphere Model,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.19932922}{10.5281/zenodo.19932922}

\bibitem{hanamura10} S. Hanamura, ``Redefining Electron Spin and Anomalous Magnetic Moment Through Harmonic Oscillation and Lorentz Contraction,'' Zenodo (2023). \href{https://doi.org/10.5281/zenodo.17764997}{10.5281/zenodo.17764997}

\bibitem{hanamura1} S. Hanamura, ``A Model of an Electron Including Two Perfect Black Bodies,'' Zenodo (2018). \href{https://doi.org/10.5281/zenodo.16759284}{10.5281/zenodo.16759284}

\bibitem{hanamura29} S. Hanamura, ``Geometric Structure of Spinorial Phase Accumulation along Thermal Geodesics,'' Zenodo (2025). \href{https://doi.org/10.5281/zenodo.18067760}{10.5281/zenodo.18067760}

\bibitem{hanamura30} S. Hanamura, ``From Curvature to Connection: Revisiting the Geometric Origin of Conservation Laws,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.18819682}{10.5281/zenodo.18819682}

\bibitem{hanamura31} S. Hanamura, ``Line Integrals as Fundamental Observables in Physics: A Unified Principle Behind the Aharonov--Bohm Effect, Berry Phase, and Wilson Loops,'' Zenodo (2026). \href{https://doi.org/10.5281/zenodo.18203433}{10.5281/zenodo.18203433}

\bibitem{ww} S. Weinberg and E. Witten, ``Limits on massless particles,'' Phys. Lett. B \textbf{96}, 59 (1980).

\bibitem{landau} L. D. Landau, ``On the angular momentum of a system of two photons,'' Dokl. Akad. Nauk SSSR \textbf{60}, 207 (1948).

\bibitem{yang} C. N. Yang, ``Selection rules for the dematerialization of a particle into two photons,'' Phys. Rev. \textbf{77}, 242 (1950).

\bibitem{klt} H. Kawai, D. C. Lewellen, and S.-H. H. Tye, ``A relation between tree amplitudes of closed and open strings,'' Nucl. Phys. B \textbf{269}, 1 (1986).

\bibitem{bcj} Z. Bern, J. J. M. Carrasco, and H. Johansson, ``Perturbative quantum gravity as a double copy of gauge theory,'' Phys. Rev. Lett. \textbf{105}, 061602 (2010).

\bibitem{peters} P. C. Peters and J. Mathews, ``Gravitational radiation from point masses in a Keplerian orbit,'' Phys. Rev. \textbf{131}, 435 (1963).

\end{thebibliography}

\end{document}
