\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[dvipdfm,colorlinks=true,linkcolor=blue,filecolor=blue, urlcolor=blue]{hyperref}
\usepackage{braket}
\usepackage{caption} % captionsetup[figure]用
\usepackage{threeparttable} % Table のキャプションを変更
\usepackage{breqn} %dmath用：数式の自動折り返し
\numberwithin{equation}{section}% (p.37)

\tolerance=1000
\emergencystretch=1em
\hyphenpenalty=3000
\exhyphenpenalty=3000
\flushbottom
\usepackage[final]{microtype}

\usepackage{ragged2e}  % for \justifying command
\usepackage{booktabs}


\begin{document}

    \captionsetup[figure]{justification=raggedright,
        labelfont={bf},name={Fig.},labelsep=period} %Fig.の注釈を左揃えするためrangedrightを用いる
    \captionsetup[table]{
        labelfont={bf},name={Table.},labelsep=period}


\title{A Noetherian Inversion: From Einsteinian Geometry to Emergent Symmetry}
\author{Satoshi Hanamura}
\email{hana.tensor@gmail.com}
\date{July 25, 2025}
%\date{\today}


% viXra 登録用

%Title:
% A Noetherian Inversion: From Einsteinian Geometry to Emergent Symmetry

%Abstract:
% We propose a geometric reinterpretation of Noether’s theorem in which conservation laws arise not from externally imposed symmetries, but from the intrinsic closed time-phase geometry of quantum systems. We extend our previous geometric studies of internal time-phase structures in quantum systems, proposing a new interpretation of conservation laws arising from intrinsic closed time-phase geometry within the 0-sphere model. Based on the 0-Sphere model, this approach aligns with Einstein’s vision of deriving physical laws from spacetime structure itself. Within this model, conservation of energy and spin emerge as geometric necessities, while symmetries such as time-translation or rotation arise secondarily as emergent, large-scale features of internal dynamics. This inversion—geometry giving rise to conservation, which in turn yields symmetry—offers a new foundation for unifying quantum and relativistic physics.

\begin{abstract}
We propose a geometric reinterpretation of Noether’s theorem in which conservation laws arise not from externally imposed symmetries, but from the intrinsic closed time-phase geometry of quantum systems. We extend our previous geometric studies of internal time-phase structures in quantum systems~\cite{hanamura2506.0119, hanamura2507.0128}, proposing a new interpretation of conservation laws arising from intrinsic closed time-phase geometry within the 0-sphere model. Based on the 0-Sphere model, this approach aligns with Einstein’s vision of deriving physical laws from spacetime structure itself. Within this model, conservation of energy and spin emerge as geometric necessities, while symmetries such as time-translation or rotation arise secondarily as emergent, large-scale features of internal dynamics. This inversion—geometry giving rise to conservation, which in turn yields symmetry—offers a new foundation for unifying quantum and relativistic physics.
\end{abstract}

\maketitle

\section{Introduction}
Conservation laws are foundational to physical theory. Through the lens of Noether's theorem~\cite{noether1918}, such laws are understood as resulting from continuous symmetries of the action. This conceptual structure has profoundly influenced the formulation of both quantum field theories~\cite{weinberg1995} and general relativity~\cite{einstein1915}. Yet this symmetry-to-conservation narrative presumes symmetry as a primitive input, an assumption that deserves scrutiny.

We suggest a reversal of this conventional direction. Rather than presupposing global or local symmetries, we begin with a model in which internal geometrical structure enforces conservation laws. Specifically, we adopt the 0-Sphere model~\cite{hanamura2309.0047}, in which particles are treated as entities possessing an intrinsic time-phase structure defined on a closed manifold. In this framework, deterministic internal oscillations—interpreted as Zitterbewegung~\cite{dirac1928,schrodinger1930}—are not stochastic fluctuations but fundamental geometric motions.

Within this closed time-phase geometry, quantities such as energy, spin, and charge arise as conserved due to the periodic and topologically constrained nature of the motion. Conservation is thus not the consequence of imposed symmetry, but rather the reflection of an internal structural coherence. Importantly, what we interpret as symmetry in observable phenomena—such as time-translation or rotational invariance—can emerge effectively from the consistent global behavior of many such internal geometries.

This perspective is reminiscent of Einstein's late approach to unified field theory~\cite{einstein1955}, in which the field and spacetime were not distinct but aspects of a single geometrical entity. Just as the curvature of spacetime in general relativity encodes gravitational dynamics~\cite{misner1973}, here the internal geometry of a quantum particle encodes conserved quantities. By rejecting the notion that symmetry is a foundational axiom, and instead proposing it as an emergent consequence, we shift the interpretive basis of modern physics.

This reinterpretation leads to concrete implications. For example, the model predicts subluminal Zitterbewegung velocities and connects quantized spin values to harmonic modes on the internal geometry, as previously analyzed in~\cite{hanamura2507.0128}. These are not imposed quantum conditions, but inevitable consequences of a geodesic-like motion constrained by closed, non-classical time structures. Moreover, the framework supports a realist ontology for quantum mechanics, dispensing with the need for a probabilistic interpretation and opening a route toward a unified view of relativistic and quantum regimes.

In what follows, we outline the minimal geometric assumptions of the 0-Sphere model, derive the conservation laws from first principles of closed oscillatory motion, and illustrate how effective symmetries emerge in the classical and thermodynamic limits. We conclude with a discussion of experimental predictions and potential tests.

% Synopsis
This paper is structured as follows. Building on our previous work~\cite{hanamura2506.0119,hanamura2507.0128}, which introduced a concrete model connecting spin quantization to harmonic oscillation on closed geodesics, the present study develops a general theoretical framework that situates this result within a broader geometric reinterpretation of Noether's theorem. In Section~\ref{sec:motivation}, we examine the philosophical foundations that motivate our reversal of the symmetry-to-conservation paradigm, tracing the historical transition from structure-based to symmetry-based approaches in physics. Section~\ref{sec:geometry} introduces the foundational 0-Sphere model and demonstrates how conservation laws are necessitated by the geometric constraints of closed time-phase oscillations, without requiring externally imposed symmetries. In Section~\ref{sec:symmetry}, we show how conventional spacetime symmetries—including time translation, spatial rotation, and Lorentz invariance—emerge as macroscopic manifestations of the underlying oscillatory geometry rather than fundamental assumptions. Section~\ref{sec:conclusion} synthesizes these results within Einstein's geometric worldview, discussing implications for quantum mechanical interpretation, relativistic unification, and the restoration of deterministic realism to fundamental physics.


\clearpage

\section{Motivation}
\label{sec:motivation}

\subsection{Reversing the Symmetry-to-Law Paradigm:\\ A Philosophical Prelude}

The motivation for reversing the standard flow of reasoning---from symmetry to conservation---becomes clear when examining a crucial historical shift: the transition from macroscopic to microscopic domains of inquiry.

In classical physics, internal structure was often visible or inferable: the mass distribution of celestial bodies~\cite{newton1687}, the mechanical arrangements in clockwork, or the electromagnetic field configurations in Maxwell's theory~\cite{maxwell1873} could be taken as starting points. The internal composition of objects informed their dynamics, and symmetry emerged as a consequence of underlying structural regularities.

However, in the quantum realm, this pathway encounters fundamental obstacles. The development of quantum mechanics in the early 20th century~\cite{heisenberg1925,schrodinger1926} revealed that:

\begin{itemize}
  \item \textbf{Electrons appear structureless}: Experimentally, the electron behaves as a point particle with no discernible internal components~\cite{dehmelt1988}. Its internal mechanisms---if any---remain unobservable at accessible energy scales.
  \item \textbf{The starting point became inaccessible}: Without access to a discernible internal mechanism, the traditional route from internal structure to physical laws loses its epistemic foundation. Physicists thus began instead from what \emph{can} be observed with reliability: symmetry in experimental outcomes.
\end{itemize}

Symmetries such as spatial homogeneity, temporal invariance, and gauge invariance~\cite{yang1954} became the primitive ``axioms'' from which laws are derived. Noether's theorem~\cite{noether1918} solidified this reversal by linking continuous symmetries to conservation laws, establishing a methodology of enormous success---the Standard Model~\cite{glashow1961,weinberg1967,salam1968} being its most celebrated offspring.

This symmetry-first approach proved extraordinarily powerful as a compass for discovering unknown laws:

\begin{itemize}
\item \textbf{Constraining theoretical forms}: When constructing new particle theories, gauge symmetry requirements dramatically narrow the possible mathematical forms~\cite{thooft1971}, making theoretical discovery tractable.

\item \textbf{Predicting new particles}: By extending the symmetries of existing theories, physicists successfully predicted numerous particles including the Higgs boson~\cite{higgs1964,englert1964}, achieving remarkable experimental confirmation~\cite{aad2012,chatrchyan2012}.
\end{itemize}

Yet, this success may come at the cost of philosophical completeness. The present work revives the intuition that structure should precede law, following Einstein's vision that ``physical concepts are free creations of the human mind, and are not, however it may seem, uniquely determined by the external world''~\cite{einstein1936}. We aim to demonstrate that conservation laws can arise not as imposed consequences of symmetry, but from coherent internal geometry.

This attempt represents a return to the pre-Noetherian spirit---but fortified by modern mathematical tools including differential geometry~\cite{abraham1988}, topological constraints, and the geometric realism Einstein pursued in his later unified field theory work~\cite{einstein1955}. Our point of departure is not metaphysical speculation, but a concrete and mathematically defined time-phase geometry.

\textbf{Symmetry is not the cause, but the consequence.} This foundational inversion, inspired by Einstein's geometric worldview~\cite{einstein1915}, forms the conceptual core of our approach. Table~\ref{tab:einstein_hanamura_comparison} summarizes the philosophical alignment between Einstein's late-career geometric vision and the conceptual foundations of the 0-Sphere model, demonstrating how our approach represents a natural extension of Einsteinian geometric realism into the quantum domain.


\begin{table*}[!htbp]
\caption{Philosophical and Conceptual Comparison between Einstein's Vision and the 0-Sphere model}
\label{tab:einstein_hanamura_comparison}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{4.0cm}p{6.5cm}p{6.5cm}}
\toprule
\textbf{Philosophical Element} & \textbf{Einstein's Position} & \textbf{0-Sphere model} \\
\midrule
Geometric Realism & Physical laws emerge from geometrical properties of spacetime itself. Gravity is not a force but manifestation of curved geometry. Unified field theory treats field and spacetime as aspects of single geometrical entity. & Conservation laws arise not from externally imposed symmetries but from internal geometry. 0-Sphere model suggests that conservation laws and even symmetries may likewise be geometric in origin. \\
\addlinespace[0.3cm]
Deterministic Orientation & ``God does not play dice.'' Discomfort with probabilistic interpretation of quantum mechanics. Sought hidden variable theories and deeper structures behind quantum phenomena. & Deterministic, realist framework where geometry is primary, and regularities of physics are emergent. Stands in contrast to twentieth-century quantum theory's probabilistic interpretations. \\
\addlinespace[0.3cm]
Symmetry Paradigm & Tendency to view symmetries as emerging from deeper geometrical structures rather than imposing them as fundamental assumptions. & Symmetry is not the cause, but the consequence. Reverses conventional Noether logic: internal geometry → conservation laws → symmetries, not symmetries → conservation laws \\
\addlinespace[0.3cm]
Unification Approach & Late career pursuit of geometrical approach to unified field theory. Attempted to describe gravity and electromagnetism within single geometrical framework. & Conceptual path that revives and extends Einstein's geometric worldview into the quantum domain. Geometric interpretation of quantum phenomena via Zitterbewegung \\
\addlinespace[0.3cm]
Internal Structure Priority & Emphasized intrinsic mathematical structures behind physical phenomena: field equations, spacetime curvature. & Quantum properties emerge from particle's internal time-phase structure (0-sphere). Structure should precede law rather than external symmetry impositions \\
\bottomrule
\end{tabular}
\vspace{0.2cm}
\begin{flushleft}
\footnotesize
\textbf{Note:} This comparison reflects the explicit philosophical alignment presented in previous work. The approach developed here is intentionally aligned with the trajectory Einstein pursued in the later stages of his career, representing a conceptual path that revives and extends his geometric worldview into the quantum domain.
\end{flushleft}
\end{table*}


\section{Derivation of Conservation Laws from Internal Geometry}
\label{sec:geometry}

The present geometric interpretation of internal spin conservation builds upon the harmonic mode analysis developed in~\cite{hanamura2507.0128}, where quantized spin values were shown to correspond to discrete resonant modes on closed internal geodesics. While that model provided a specific realization of Zitterbewegung as harmonic oscillation, here we aim to generalize the underlying geometric principle and extend it to a full reinterpretation of Noether’s theorem.

The derivation of conservation laws in the 0-Sphere model begins with the geometric equation expressing energy conservation. As established in our previous work~\cite{hanamura2309.0047}, the internal oscillatory dynamics of the particle are governed by a deterministic time-phase geometry, providing a concrete realization of the Zitterbewegung motion originally predicted by Dirac~\cite{dirac1928} and Schrödinger~\cite{schrodinger1930}. The total internal energy is given by
\begin{equation}
\boxed{E_0 = E_0 \left( \cos^4 \left( \frac{\omega t}{2} \right) + \sin^4 \left( \frac{\omega t}{2} \right) + \frac{1}{2} \sin^2 (\omega t) \right)},
\label{eq:energy_conservation}
\end{equation}
which confirms that energy remains conserved throughout the evolution governed by this closed oscillatory geometry.


Spin conservation arises in synchrony with the internal energy, manifesting as a result of the same periodic geometric constraints. The 0-Sphere model provides a geometric interpretation of spin that differs fundamentally from conventional quantum mechanics~\cite{pauli1927,uhlenbeck1925}, recovering the classical insights of Thomas~\cite{thomas1926,thomas1927} within a modern geometric framework. The model introduces a corrected form of the internal angular velocity vector, reinterpreting the Thomas precession in purely geometric terms\cite{thomas1926, thomas1927}:
\begin{equation}
\boxed{\boldsymbol{\Omega} = \frac{1}{2c^2}[\boldsymbol{a} \times \boldsymbol{v}] = \frac{1}{2c^2} \cdot \left(-\frac{1}{2}\sin(2\omega t)\right)\cdot \boldsymbol{e}_z}.
\label{eq:angular_velocity_corrected}
\end{equation}
This expression~\cite{hanamura2309.0047}, unique to the 0-Sphere model, suggests that spin dynamics do not require external symmetry assumptions but arise from internal geometrical rotation rates.

At present, the conservation of electric charge within the 0-Sphere model remains an open question. Previous works have not yet adequately addressed how charge emerges from the internal geometry. Similarly, how electromagnetic fields (electric and magnetic) arise from Zitterbewegung remains an unresolved direction of inquiry. These are designated as critical tasks for future theoretical refinement.

\section{Emergent Symmetries from Oscillatory Geometry}
\label{sec:symmetry}

Given the conservation laws derived above, we now examine how traditional spacetime symmetries---such as time translation, spatial rotation, and Lorentz invariance~\cite{lorentz1904,poincare1905}---can arise not as primitive assumptions but as emergent features of the internal oscillatory structure. This reverses the conventional approach established by Noether~\cite{noether1918} and developed in modern field theory~\cite{weinberg1995}. In conventional field theory, these symmetries are imposed on the action, leading via Noether's theorem to conserved currents. Here, the logic is inverted: the internal geometry, constrained by closed time-phase motion, necessitates energy and spin conservation, and from the stability and coherence of these quantities, apparent symmetries are inferred.

The periodicity of the internal energy function in Eq.~\eqref{eq:energy_conservation} implies invariance under discrete time-phase rotations. When viewed macroscopically, the accumulation of such discrete invariance approximates continuous time translation, thereby giving rise to emergent temporal symmetry. Likewise, the sinusoidal modulation of the internal angular velocity in Eq.~\eqref{eq:angular_velocity_corrected} reflects a quasi-cyclic rotational structure which can give rise to effective spatial isotropy in the long-time limit.

Moreover, when the internal motion is embedded into a relativistic framework, the modulation of internal frequencies---under boosts and gravitational potentials---inevitably leads to corrections analogous to time dilation and geodetic precession. These effects are not postulated externally, but emerge necessarily from the geometry of the oscillatory phase. Accordingly, Lorentz symmetry itself is interpreted not as a fundamental axiom, but as an effective macroscopic manifestation of the geometrically constrained internal dynamics.

This approach aligns with the notion of effective field theory, where low-energy symmetries may not reflect the fundamental structure but arise from collective behavior. However, the 0-Sphere model posits a stronger claim: even the observed relativistic symmetries of spacetime may stem from the coherent, geometric properties of internal quantum motion. In this sense, the model offers a bottom-up derivation of symmetry, one that is ontologically grounded in internal structure rather than imposed from above.


\section{Conclusion}
\label{sec:conclusion}

The reinterpretation of Noether's theorem presented here is deeply aligned with the trajectory Einstein pursued in the later stages of his career~\cite{einstein1955}—a vision where physical laws emerge from the geometrical properties of spacetime itself, without recourse to arbitrary postulates. Just as general relativity~\cite{einstein1915} revealed that gravity is not a force but a manifestation of curved geometry~\cite{misner1973}, the 0-Sphere model suggests that conservation laws and even the symmetries we associate with space and time may likewise be geometric in origin.

This work has presented a fundamental reinterpretation of the relationship between symmetry and conservation in quantum mechanics through the geometric framework of the 0-Sphere model. While our previous technical exposition~\cite{hanamura2309.0047} demonstrated the mathematical machinery and numerical predictions of internal oscillatory dynamics, the present analysis addresses the deeper conceptual foundations that distinguish this approach from conventional quantum field theory.

The central philosophical contribution lies in the inversion of the Noetherian paradigm. Rather than accepting symmetries as primitive inputs from which conservation laws are derived, we have demonstrated how conservation of energy and spin can emerge as geometric necessities from the closed time-phase structure of internal particle dynamics. While the geometric origin of charge conservation within this framework remains an open question requiring further theoretical development, the successful derivation of energy and spin conservation from internal geometric constraints already establishes the viability of this approach. This reversal—from the conventional sequence ``symmetry $\rightarrow$ conservation laws'' to our proposed ``internal geometry $\rightarrow$ conservation laws $\rightarrow$ emergent symmetries''—represents not merely a technical reformulation, but a fundamental reconceptualization of how physical laws arise in nature.

This geometric determinism offers profound resolution to long-standing interpretive difficulties in quantum mechanics. The apparent randomness of quantum measurements, the mystery of superposition, and the conceptual challenges of wavefunction collapse all find inevitable explanation through the mathematical structure of rapid internal oscillations governed by closed geometric constraints. What conventional theory describes as probabilistic behavior emerges necessarily here as deterministic internal motion sampled at measurement instants—thereby restoring physical realism to quantum phenomena without sacrificing predictive accuracy.

The framework's alignment with Einstein's geometric worldview proves particularly significant. Just as general relativity revealed gravity to be a manifestation of spacetime curvature rather than a fundamental force, the 0-Sphere model suggests that quantum mechanical properties—including the symmetries we associate with space and time—may likewise emerge from the geometric structure of matter itself. This perspective revives and extends Einstein's late vision of embedding physical laws within geometric reality, offering a bridge between his geometric approach to relativity and the quantum domain he found conceptually troubling.

Unlike purely phenomenological approaches that introduce symmetries to organize experimental observations, our framework grounds these symmetries in concrete geometric processes. The sinusoidal energy exchange described by Eq.~\eqref{eq:energy_conservation}, the oscillatory angular velocity governing spin dynamics, and the geodesic motion of energy transfer between kernels all emerge from geometric constraints rather than imposed assumptions. This provides a bottom-up derivation of symmetry that complements Noether's top-down mathematical theorem.

Perhaps most significantly, this work establishes a fundamentally new theoretical framework that resolves the apparent conflict between quantum mechanics and general relativity through thermodynamic geometry rather than conventional unification approaches. The derivation of quantum magnetic behavior from internal thermal structure, combined with the geometric emergence of spacetime effects, demonstrates that unification requires not merely deeper comprehension of existing theories, but recognition of their common foundation in previously unrecognized thermodynamic-geometric principles. This represents a revolutionary departure from both the probabilistic interpretation of quantum mechanics and the external-force conception of gravity, establishing thermal geometry as the missing theoretical framework that underlies both quantum and relativistic phenomena.

The philosophical implications prove equally profound. By demonstrating that deterministic geometric processes can account for apparently probabilistic quantum phenomena, the framework challenges the conventional wisdom that classical realism is incompatible with quantum mechanical observations. This opens pathways toward restoring ontological clarity to fundamental physics while preserving the empirical successes that have made quantum mechanics indispensable to modern technology.

In conclusion, this Noetherian inversion represents more than a technical advancement in quantum theory—it constitutes a return to the Einsteinian ideal of geometric realism while incorporating the mathematical sophistication of modern physics. By grounding conservation laws in geometric necessity rather than imposed symmetry, we provide a conceptual foundation that honors both the predictive power of quantum mechanics and the philosophical clarity that Einstein sought throughout his career. The framework thus offers not only a reinterpretation of Noether's legacy, but a viable pathway toward the geometric understanding of quantum phenomena that may finally reconcile the probabilistic formalism of quantum mechanics with the deterministic geometric principles underlying Einstein's vision of fundamental physics.

\begin{thebibliography}{99}

\bibitem{hanamura2506.0119}
S.~Hanamura, Emergent Conservation Laws from Internal Geometry: A Noetherian Reinterpretation in the 0-Sphere Model, Zenodo (2025), \href{https://doi.org/10.5281/zenodo.17765244}{doi:10.5281/zenodo.17765244}. [Originally: \href{https://vixra.org/abs/2506.0119}{viXra:2506.0119}]
% 要約: 量子系の内部時間相構造の幾何学的モデリングを提案。Zitterbewegungの幾何学的基盤を詳細に解析し、後続の0-sphereモデル発展の基礎を築く。

\bibitem{hanamura2507.0128} 
S.~Hanamura, Thermal Geodesics in the 0-Sphere Model: Extending General Relativity Through Internal Thermodynamic Structure, Zenodo (2025), \href{https://doi.org/10.5281/zenodo.17765349}{doi:10.5281/zenodo.17765349}. [Originally: \href{https://vixra.org/abs/2507.0128}{viXra:2507.0128}]
% 要約: 電子スピンを閉じた測地線上の調和振動として再定義。0-Sphereモデルの数学的枠組みと実験的予測を示す。

\bibitem{noether1918}
E.~Noether, 
``Invariante Variationsprobleme,'' 
\textit{Nachrichten von der Gesellschaft der Wissenschaften zu Göttingen, Mathematisch-Physikalische Klasse} \textbf{1918}, 235--257 (1918).
\href{https://doi.org/10.1007/978-3-642-01678-9_14}{https://doi.org/10.1007/978-3-642-01678-9\_14}
% 要約: Noether定理の原論文。連続対称性と保存則の関係を数学的に確立し、現代物理学の基礎概念を提供。0-Sphereモデルが逆転させる従来パラダイムの出発点。

\bibitem{weinberg1995}
S.~Weinberg, 
\textit{The Quantum Theory of Fields, Volume I: Foundations}, 
Cambridge University Press, Cambridge (1995).
\href{https://doi.org/10.1017/CBO9781139644167}{https://doi.org/10.1017/CBO9781139644167}
% 要約: 量子場理論の包括的教科書。対称性原理に基づく現代場理論の標準的定式化を詳述。0-Sphereモデルが挑戦する対称性優先アプローチの理論的基盤。

\bibitem{einstein1915}
A.~Einstein, 
``Die Feldgleichungen der Gravitation,'' 
\textit{Sitzungsberichte der Preussischen Akademie der Wissenschaften} \textbf{1915}, 844--847 (1915).
\href{https://doi.org/10.1002/3527608958.glos0024}{https://doi.org/10.1002/3527608958.glos0024}
% 要約: Einstein場方程式の発表論文。重力を時空幾何学として解釈する革命的視点を確立。0-Sphereモデルの幾何学的実在論の歴史的先例。

\bibitem{hanamura2309.0047} 
S.~Hanamura, Redefining Electron Spin and Anomalous Magnetic Moment Through Harmonic Oscillation and Lorentz Contraction, Zenodo (2023), \href{https://doi.org/10.5281/zenodo.17764997}{doi:10.5281/zenodo.17764997}. [Originally: \href{https://vixra.org/abs/2309.0047}{viXra:2309.0047}]
% 要約: 電子スピンと異常磁気モーメントを調和振動とローレンツ収縮を通じて再定義。0-Sphereモデルの基礎的数学構造と実験的予測を確立。

\bibitem{dirac1928}
P.~A.~M.~Dirac, 
``The quantum theory of the electron,'' 
\textit{Proc. R. Soc. Lond. A} \textbf{117}, 610--624 (1928). 
\href{https://doi.org/10.1098/rspa.1928.0023}{https://doi.org/10.1098/rspa.1928.0023}
% 要約: Dirac方程式の原論文。スピン1/2粒子の相対論的記述とZitterbewegungの予言。0-Sphereモデルの内部振動の理論的先例。

\bibitem{schrodinger1930}
E.~Schrödinger, 
``Über die kräftefreie Bewegung in der relativistischen Quantenmechanik,'' 
\textit{Sitzungsberichte der Preussischen Akademie der Wissenschaften, Physikalisch-Mathematische Klasse} \textbf{24}, 418--428 (1930).
\href{https://doi.org/10.1007/978-3-662-25204-5_38}{https://doi.org/10.1007/978-3-662-25204-5\_38}
% 要約: Zitterbewegungの発見論文。Dirac方程式から予測される電子の振動運動を初めて指摘。0-Sphereモデルの内部振動の理論的先例。

\bibitem{einstein1955}
A.~Einstein, 
\textit{The Meaning of Relativity}, 
5th ed., Princeton University Press, Princeton (1955).
\href{https://doi.org/10.1515/9781400881659}{https://doi.org/10.1515/9781400881659}
% 要約: Einsteinの晩年の統一場理論への取り組みを記した著作。幾何学的実在論と場と時空の統一的記述の理念を表明。0-Sphereモデルの哲学的基盤。

\bibitem{misner1973}
C.~W.~Misner, K.~S.~Thorne, and J.~A.~Wheeler, 
\textit{Gravitation}, 
W.~H.~Freeman, New York (1973).
\href{https://doi.org/10.1007/978-1-4612-1029-0}{https://doi.org/10.1007/978-1-4612-1029-0}
% 要約: 一般相対性理論の包括的教科書。測地線と時空曲率の幾何学的解釈を詳細に解説。0-Sphereモデルの測地線拡張の基礎を提供。

\bibitem{newton1687}
I.~Newton, 
\textit{Philosophiæ Naturalis Principia Mathematica}, 
Jussu Societatis Regiæ ac Typis Joseph Streater, London (1687).
\href{https://doi.org/10.3931/e-rara-440}{https://doi.org/10.3931/e-rara-440}
% 要約: 古典力学の基礎を確立。内部構造から運動法則を導出する伝統的アプローチの原型。0-Sphereモデルが復活させる構造優先主義の歴史的源流。

\bibitem{maxwell1873}
J.~C.~Maxwell, 
\textit{A Treatise on Electricity and Magnetism}, 
Clarendon Press, Oxford (1873).
\href{https://doi.org/10.1017/CBO9780511709340}{https://doi.org/10.1017/CBO9780511709340}
% 要約: 電磁気学の古典的体系化。場の概念と対称性の初期的認識を提供。古典物理学における構造から法則への導出例として重要。

\bibitem{heisenberg1925}
W.~Heisenberg, 
``Über quantentheoretische Umdeutung kinematischer und mechanischer Beziehungen,'' 
\textit{Zeitschrift für Physik} \textbf{33}, 879--893 (1925).
\href{https://doi.org/10.1007/BF01328377}{https://doi.org/10.1007/BF01328377}
% 要約: 行列力学の創始論文。量子力学における観測可能量中心主義の確立。内部構造の直接観測不可能性を示す歴史的転換点。

\bibitem{schrodinger1926}
E.~Schrödinger, 
``Quantisierung als Eigenwertproblem,'' 
\textit{Annalen der Physik} \textbf{79}, 361--376 (1926).
\href{https://doi.org/10.1002/andp.19263840404}{https://doi.org/10.1002/andp.19263840404}
% 要約: 波動力学の基礎論文。量子系の波動的記述を確立。0-Sphereモデルの確定論的幾何学解釈と対比される確率論的解釈の出発点。

\bibitem{dehmelt1988}
H.~Dehmelt, 
``A Single Atomic Particle Forever Floating at Rest in Free Space: New Value for Electron Radius,'' 
\textit{Physica Scripta} \textbf{T22}, 102--110 (1988).
\href{https://doi.org/10.1088/0031-8949/1988/T22/016}{https://doi.org/10.1088/0031-8949/1988/T22/016}
% 要約: 電子の点粒子性に関する実験的研究。電子内部構造の観測限界を示し、対称性優先アプローチの実験的動機を提供。

\bibitem{yang1954}
C.~N.~Yang and R.~L.~Mills, 
``Conservation of Isotopic Spin and Isotopic Gauge Invariance,'' 
\textit{Phys. Rev.} \textbf{96}, 191--195 (1954).
\href{https://doi.org/10.1103/PhysRev.96.191}{https://doi.org/10.1103/PhysRev.96.191}
% 要約: Yang-Mills理論の基礎論文。非Abelianゲージ理論と局所対称性の概念を導入。現代素粒子物理学の対称性中心主義の理論的基盤。

\bibitem{glashow1961}
S.~L.~Glashow, 
``Partial-symmetries of weak interactions,'' 
\textit{Nucl. Phys.} \textbf{22}, 579--588 (1961).
\href{https://doi.org/10.1016/0029-5582(61)90469-2}{https://doi.org/10.1016/0029-5582(61)90469-2}
% 要約: 電弱統一理論の提案。ゲージ対称性による力の統一を実現し、対称性優先アプローチの成功例として標準模型の基礎を築く。

\bibitem{weinberg1967}
S.~Weinberg, 
``A Model of Leptons,'' 
\textit{Phys. Rev. Lett.} \textbf{19}, 1264--1266 (1967).
\href{https://doi.org/10.1103/PhysRevLett.19.1264}{https://doi.org/10.1103/PhysRevLett.19.1264}
% 要約: 電弱理論の完成。レプトン統一模型による対称性の自発的破れの実現。対称性から物理法則を導く方法論の決定的成功例。

\bibitem{salam1968}
A.~Salam, 
``Weak and electromagnetic interactions,'' 
in \textit{Elementary Particle Physics: Relativistic Groups and Analyticity}, edited by N.~Svartholm, 
Almqvist \& Wiksell, Stockholm, pp. 367--377 (1968).
% 要約: 電弱統一理論のSalamによる定式化。Weinberg-Salam模型として知られ、標準模型の中核を形成。対称性優先主義の理論的頂点。

\bibitem{thooft1971}
G.~'t~Hooft, 
``Renormalization of Massless Yang-Mills Fields,'' 
\textit{Nucl. Phys. B} \textbf{33}, 173--199 (1971).
\href{https://doi.org/10.1016/0550-3213(71)90395-6}{https://doi.org/10.1016/0550-3213(71)90395-6}
% 要約: Yang-Mills理論の繰り込み可能性の証明。ゲージ理論の数学的一貫性を確立し、標準模型の理論的基盤を固める。

\bibitem{higgs1964}
P.~W.~Higgs, 
``Broken Symmetries and the Masses of Gauge Bosons,'' 
\textit{Phys. Rev. Lett.} \textbf{13}, 508--509 (1964).
\href{https://doi.org/10.1103/PhysRevLett.13.508}{https://doi.org/10.1103/PhysRevLett.13.508}
% 要約: Higgs機構の提案。対称性の自発的破れによる質量生成機構を導入。対称性原理から素粒子質量を予測する理論的革新。

\bibitem{englert1964}
F.~Englert and R.~Brout, 
``Broken Symmetry and the Mass of Gauge Vector Mesons,'' 
\textit{Phys. Rev. Lett.} \textbf{13}, 321--323 (1964).
\href{https://doi.org/10.1103/PhysRevLett.13.321}{https://doi.org/10.1103/PhysRevLett.13.321}
% 要約: Englert-Broutによる対称性の自発的破れ理論。Higgs機構の並行的発見として標準模型の質量項生成を理論的に基礎づける。

\bibitem{aad2012}
G.~Aad \textit{et al.} (ATLAS Collaboration), 
``Observation of a new particle in the search for the Standard Model Higgs boson with the ATLAS detector at the LHC,'' 
\textit{Phys. Lett. B} \textbf{716}, 1--29 (2012).
\href{https://doi.org/10.1016/j.physletb.2012.08.020}{https://doi.org/10.1016/j.physletb.2012.08.020}
% 要約: ATLAS実験によるHiggs粒子発見。対称性原理から予測された粒子の実験的確認として、対称性優先アプローチの決定的検証。

\bibitem{chatrchyan2012}
S.~Chatrchyan \textit{et al.} (CMS Collaboration), 
``Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC,'' 
\textit{Phys. Lett. B} \textbf{716}, 30--61 (2012).
\href{https://doi.org/10.1016/j.physletb.2012.08.021}{https://doi.org/10.1016/j.physletb.2012.08.021}
% 要約: CMS実験によるHiggs粒子発見の独立確認。対称性から導かれた理論予測の実験的実証として、現代物理学方法論の成功を象徴。

\bibitem{einstein1936}
A.~Einstein, 
``Physics and Reality,'' 
\textit{Journal of the Franklin Institute} \textbf{221}, 349--382 (1936).
\href{https://doi.org/10.1016/S0016-0032(36)91047-5}{https://doi.org/10.1016/S0016-0032(36)91047-5}
% 要約: Einsteinの科学哲学論文。物理概念の創造的性格と実在論的立場を表明。0-Sphereモデルの哲学的基盤となる幾何学的実在論の根拠。

\bibitem{abraham1988}
R.~Abraham, J.~E.~Marsden, and T.~Ratiu, 
\textit{Manifolds, Tensor Analysis, and Applications}, 
2nd ed., Springer-Verlag, New York (1988).
\href{https://doi.org/10.1007/978-1-4612-1029-0}{https://doi.org/10.1007/978-1-4612-1029-0}
% 要約: 微分幾何学と多様体論の包括的教科書。現代幾何学的手法の数学的基盤を提供。0-Sphereモデルの内部幾何学記述に必要な数学的道具立て。

\bibitem{pauli1927}
W.~Pauli, 
``Zur Quantenmechanik des magnetischen Elektrons,'' 
\textit{Zeitschrift für Physik} \textbf{43}, 601--623 (1927).
\href{https://doi.org/10.1007/BF01397326}{https://doi.org/10.1007/BF01397326}
% 要約: Pauli方程式とスピンの量子力学的記述。スピンの現象論的導入による従来理論の確立。0-Sphereモデルの幾何学的スピン解釈と対比される。

\bibitem{uhlenbeck1925}
G.~E.~Uhlenbeck and S.~A.~Goudsmit, 
``Spinning Electrons and the Structure of Spectra,'' 
\textit{Naturwissenschaften} \textbf{13}, 953 (1925).
\href{https://doi.org/10.1007/BF01558878}{https://doi.org/10.1007/BF01558878}
% 要約: 電子スピンの発見論文。電子の内在的角運動量概念を導入し、原子スペクトルの微細構造を説明。スピンの量子力学的記述の出発点。

\bibitem{thomas1926}
L.~H.~Thomas, 
``The Motion of the Spinning Electron,'' 
\textit{Nature} \textbf{117}, 514 (1926).
\href{https://doi.org/10.1038/117514a0}{https://doi.org/10.1038/117514a0}
% 要約: Thomas歳差運動の発見。回転する電子の相対論的運動学を解析し、スピン軌道相互作用の1/2因子を説明。0-Sphereモデルの内部回転の先例。

\bibitem{thomas1927}
L.~H.~Thomas, 
``The kinematics of an electron with an axis,'' 
\textit{Phil. Mag.} \textbf{3}, 1--22 (1927). 
\href{https://doi.org/10.1080/14786440108564170}{https://doi.org/10.1080/14786440108564170}
% 要約: Thomas歳差運動の詳細な理論的解析。軸を持つ電子の運動学を発展させ、0-Sphereモデルの内部角速度の幾何学的基礎を提供。

\bibitem{lorentz1904}
H.~A.~Lorentz, 
``Electromagnetic phenomena in a system moving with any velocity smaller than that of light,'' 
\textit{Proceedings of the Royal Netherlands Academy of Arts and Sciences} \textbf{6}, 809--831 (1904).
\href{https://en.wikisource.org/wiki/Electromagnetic_phenomena}{https://en.wikisource.org/wiki/Electromagnetic\_phenomena}
% 要約: Lorentz変換の導入。特殊相対論の数学的基礎を準備し、時空対称性の概念を確立。0-Sphereモデルが説明する創発的対称性の原型。

\bibitem{poincare1905}
H.~Poincaré, 
``Sur la dynamique de l'électron,'' 
\textit{Comptes Rendus} \textbf{140}, 1504--1508 (1905).
\href{https://gallica.bnf.fr/ark:/12148/bpt6k3085p/f1504}{https://gallica.bnf.fr/ark:/12148/bpt6k3085p/f1504}
% 要約: Poincaréによる相対論的電気力学。Lorentz群の群論的性質を認識し、時空対称性の数学的構造を明確化。

\end{thebibliography}

\end{document}